### 2024-02-10 outputs/paper/paper.qmd
file structure set up

---
title: "A Modest Proposal for Developing Better Experience with TTC Subway"
title-block-banner: true
abstract: ""
thanks: "Code and data supporting this analysis are available at: https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
author: "Terry Tu"
date: today
date-format: long
format: pdf
toc: true
toc-depth: 1
number-sections: true
bibliography: references.bib
link-citations: true
---

## Reference

### 2024-02-10 outputs/paper/paper.qmd
uploaded dataset

@@
 ---
-title: "A Modest Proposal for Developing Better Experience with TTC Subway"
+title: "Student Replication for \"Money Illusion\""
 title-block-banner: true
@@
 thanks: "Code and data supporting this analysis are available at: https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
-author: "Terry Tu"
+author: "Terry Tu, Jingyi Shen, Yaning Jin "
 date: today

### 2024-02-10 outputs/paper/paper.qmd
updated references

--- 2024-02-10 outputs/paper/paper.qmd
@@
 toc: true
-toc-depth: 1
+toc-depth: 2
 number-sections: true
@@
 
+## Introduction
+
+## Data
+
 ## Reference

### 2024-02-12 outputs/paper/paper.qmd
fixed minor issue

--- 2024-02-10 outputs/paper/paper.qmd
@@
 ---
-title: "A Modest Proposal for Developing Better Experience with TTC Subway"
+title: "Student Replication for \"Money Illusion\""
 title-block-banner: true
-abstract: ""
-thanks: "Code and data supporting this analysis are available at: https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
-author: "Terry Tu"
+abstract: "Money illusion as the tendency to overlook the impact of inflation which  focusing on nominal values identified by Shafir, Diamond, and Tversky (1997).
+This study reproduce four scenarios from research where participants face financial decisions influenced by money illusion in various situations such as earnings, transactions, and contracts,under the background of Brazilian context, where in various situations such as transactions, transactions and earnings that participants face financial decisions influenced by money illusion.
+The cross-sectional and pre-registered research is based on 372 Brazilian participants in mobile phones or computers by using chi-square tests assessed money illusion.
+The results indicate that participants' tend to choose financially advantages opportunities which  influenced by the framing of terms (real, nominal, or neutral).
+After we replicate across all four scenarios, the findings suggest that the money illusion effect  transcend cultural boundaries, supported by replication within a different background of cultural context."
+thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
+author: "Terry Tu, Jingyi Shen, Yaning Jin "
 date: today
@@
 
+## Introduction
+Money illusion refers to a cognitive bias where individuals tend to assess the value of money solely based on its nominal value.
+The real value of money is the nominal value of money plus the inlation rate.
+thereby overlooking the impact of inflation.
+This bias can lead to various consequences, such as reluctance to sell assets due to perceived nominal losses, misunderstanding wage increases, and more.
+
+The influential 1997 study by Shafir and colleagues[@shafir1997money] has significantly impacted on economic psychology and behavioral economics which introduced the concept of money illusion.
+The authors argued that money illusion could explain phenomena like inflexible wages and contracts which contrary to traditional economic theories assuming rationality in decision-making.
+
+When shopping, people often ignore information that is clearly distorted by inflation and impulsively raise the psychological price above the actual price, which is the money illusion.
+Money illusions can lead potential buyers to believe that house prices will always rise, and thus that real estate is a good investment.
+Robert J.
+Shiller, a professor of economics at Yale University in the United States, believes that it is the false logic caused by the monetary illusion that led to the real estate bubble, "people mostly only remember the price of a few years ago when they bought a house, but often forget the price of other goods, andmistakenly believe that house prices have risen more than other prices." Thus exaggerating the investment potential of real estate"[@Shiller].
+
+For decades, economists have debated whether the money illusion is real or, more generally, whether there are irrational influences in economic transactions.
+Milton Friedman, the famous monetary theorist, assumed that employers and consumers were rational, paying wages or buying goods with inflation in mind.
+In other words, they can accurately judge the true value of a commodity[@friedman2010milton].
+
+Recognizing the importance of testing theories in different contexts for generalizability, our study aims to investigate the presence of the money illusion effect in a Brazilian cultural setting.
+Specifically, we aim to replicate four problems proposed by Shafir and colleagues [@shafir1997money]and examine if Brazilians exhibit money illusion biases.
+
+In this paper, our hypothesis are across all four problems: in problem 1, individuals inclined to perceive wage increases significantly in real term even if it is small in nominal terms; In problem 2, individuals will evaluate house deals based on nominal gains rather than real gains; In problem 3, participants will be less likely to purchase new items rather than second hand items when prices increase nominally; In problem 4, individuals might prefer riskier contracts in real terms over safer options presented in nominal terms.
+
+## Data
+
+## Results
+
+## Conclusion
+
 ## Reference

### 2024-02-12 outputs/paper/paper.qmd
added data section

@@
 ## Introduction
+
 Money illusion refers to a cognitive bias where individuals tend to assess the value of money solely based on its nominal value.
@@
 
+The raw dataset for our study, derived from the replication of the "Money Illusion" effect among Brazilian researchers [@Santiago_Feldman_Ferreira_Batistuzzo_Fatori_Seda_Bastos_2023], is archived and accessible through the Open Science Framework (OSF).
+This dataset encompasses the complete set of responses collected through our online survey, including socio-demographic information, responses to the money illusion problems, and verification question answers.
+Interested researchers can access the dataset for further analysis or replication studies at the following URL: https://osf.io/48pqu/.
+
+### Dataset Description
+
+The data were collected via an online survey platform and include a range of variables:
+
+**Socio-demographic Information**: Participants provided details about their educational background, area of study (if applicable), average monthly family income, and the number of people living off this income.
+
+**Economic Decision-Making Scenarios**: The core of the dataset revolves around responses to hypothetical scenarios designed to assess susceptibility to the money illusion.
+These scenarios include decisions about signing contracts under inflation uncertainty, and buying or selling items after an inflation increase, reflecting real-life economic decisions that people might face.
+
+**Temporal and Response Details**: Each record includes timestamps for the start and end of the survey, the type of response, progress through the survey, duration in seconds, and completion status.
+
+**Verification Questions**: To ensure participants understood the scenarios accurately, verification questions were included.
+These serve as a quality control measure, filtering for data quality and comprehension.
+
+### Data Analysis Tools
+
+The data analysis was performed using R [@r], a powerful open-source statistical programming language.
+Key packages from the tidyverse collection [@rTidyverse] were employed to streamline data manipulation, visualization, and analysis processes.
+These packages include ggplot2 [@rGgplot2] for creating advanced graphics, dplyr [@rDplyr] for data manipulation, readr [@rReadr] for its robust data reading functionalities, here [@R-here] is used to avoid file path issue, and knitr [@rKnitr] for dynamic report generation.
+
 ## Results

### 2024-02-13 outputs/paper/paper.qmd
added data cleaning steps

@@
 ---
-title: "Student Replication for \"Money Illusion\""
+title: "Replicating the \"Money Illusion\" Effect: Exploring Gender Influences within a Brazilian Sample"
 title-block-banner: true
@@
 ---
+
+```{r setup, include=FALSE, message=FALSE}
+# Un-comment these lines for missing packages
+# install.packages("lubridate")
+# install.packages("dplyr")
+# install.packages("ggplot2")
+# install.packages("here")
+# install.packages("readr")
+# install.packages("tidyverse")
+# install.packages("readxl")
+
+## Import nessasay libraries
+library(readxl)
+library(ggplot2)
+library(dplyr)
+library(tidyverse)
+library(here)
+library(readr)
+knitr::opts_chunk$set(echo = FALSE)
+```
 
@@
 
+```{r include=FALSE, message=FALSE}
+# read the data file and store it in the 'data' variable
+data <- readxl::read_excel(here("inputs", "data", "money_data_raw.xlsx"))
+```
+
 ### Dataset Description
@@
 
+### Data Cleaning
+
+### Data Sample
+
+```{r table1, echo=FALSE}
+knitr::kable(head(data, 6), 
+             caption = "Sample of the Cleaned TTC Subway Delay Data",
+             format = "markdown")
+```
+
+### Measurement
+
 ## Results
+
+### Problem 1: 
+```{r fig-problem1, echo=FALSE, fig.cap=""}
+
+```
 

### 2024-02-13 scripts/01-cleanup-data.R

@@ -1,0 +1,47 @@
+# Load necessary libraries
+# install.packages("dplyr")
+# install.packages("readxl")
+# install.packages("here")
+
+library(readxl)
+library(dplyr)
+library(here)
+
+# Use the `here` function to specify file paths relative to the project root
+# These variables are used to store the file path to get the file before data cleaning
+# and save the file after data cleaning
+input_file_path <- here("inputs", "data", "money_data_raw.xlsx")
+output_file_path <- here("outputs", "data", "cleaned_money_data_raw.csv")
+
+# Read the raw dataset
+raw_data <- readxl::read_excel(input_file_path)
+
+# Remove the first row from the dataset
+cleaned_data <- raw_data %>% 
+  slice(-1)
+
+# Remove unessasay columns for this study
+# We only want the gender and choices columns
+cleaned_data <- cleaned_data %>%
+  select(
+    -idade, 
+    -gênero_3_TEXT, 
+    -decl_racial, 
+    -decl_racial_5_TEXT, 
+    -escolaridade, 
+    -escolaridade_transf, 
+    -área_estudo, 
+    -curso, 
+    -cidade_bairro_1, 
+    -renda, 
+    -renda_e_pessoas,
+    -verif_maria,
+    -`setal1997-funnel`
+  )
+
+# Remove rows where gender is NA
+cleaned_data <- cleaned_data %>%
+  filter(!is.na(gênero))
+
+# Optionally, save the cleaned dataset to a CSV file
+write.csv(cleaned_data, output_file_path, row.names = FALSE)

### 2024-02-13 outputs/paper/paper.qmd
added new plots

@@
 # read the data file and store it in the 'data' variable
-data <- readxl::read_excel(here("inputs", "data", "money_data_raw.xlsx"))
+data <- read_csv(here("outputs", "data", "cleaned_money_data.csv"))
 ```
@@
 ```{r table1, echo=FALSE}
-knitr::kable(head(data, 6), 
-             caption = "Sample of the Cleaned TTC Subway Delay Data",
+selected_data <- data %>%
+  select(1:2, (ncol(data)-2):ncol(data))
+
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Money Illusion Data for Question 1",
+             format = "markdown")
+```
+```{r table2, echo=FALSE}
+selected_data <- data %>%
+  select(1:2, 12:14)
+
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Money Illusion Data for Question 2",
+             format = "markdown")
+```
+
+```{r table3, echo=FALSE}
+selected_data <- data %>%
+  select(1:2, 7:9)
+
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Money Illusion Data for Question 3",
+             format = "markdown")
+```
+
+```{r table4, echo=FALSE}
+selected_data <- data %>%
+  select(1:5)
+
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Money Illusion Data for Question 4",
              format = "markdown")
@@
 
+\newpage
+
 ## Results
@@
 ### Problem 1: 
-```{r fig-problem1, echo=FALSE, fig.cap=""}
+```{r echo=FALSE}
+# Function to create plot based on gender
+create_gender_plot <- function(gender, data) {
+  # Translate 'gênero' to English and filter data for the specific gender
+  gender_data <- data %>%
+    mutate(gênero = recode(gênero, 'Mulher' = 'Female', 'Homem' = 'Male')) %>%
+    filter(gênero == gender) %>%
+    gather(key = "category", value = "choice", economicam, felicidade, atratividade_trab) %>%
+    filter(!is.na(choice))
+
+  # Calculate the percentage of non-NA responses for each category
+  freq_data <- gender_data %>%
+    count(category, choice) %>%
+    group_by(category) %>%
+    mutate(Percentage = n / sum(n) * 100) %>%
+    ungroup()
+
+  # Modify the category names to translate to English
+  freq_data$category <- recode(freq_data$category,
+                               "economicam" = "Economic Terms",
+                               "felicidade" = "Happiness",
+                               "atratividade_trab" = "Job Attractiveness")
+
+  # Creating the plot with ggplot2
+  plot <- ggplot(data = freq_data, aes(x = category, y = Percentage, fill = choice)) +
+    geom_bar(stat = "identity", position = position_dodge(), color = "black") +
+    scale_fill_brewer(palette = "Pastel1") +
+    labs(
+         title = paste("Choices Distribution for", gender, "in Money Illusion Experiment 1"),
+         x = "Condition",
+         y = "Percentage"
+    ) +
+    theme(
+          legend.position = "bottom",
+          axis.text.x = element_text(angle = 45, hjust = 1),
+          plot.title = element_text(hjust = 0.5),
+          plot.caption = element_text(hjust = 0.5)
+    ) +
+    ylim(0, 100)
+
+  # Return the plot
+  return(plot)
+}
+```
+
+```{r fig-problem1-female, echo=FALSE, fig.cap="The percentage of female participants' choices within each condition in problem 1."}
+# Create plots for 'Female'
+plot_female <- create_gender_plot("Female", data)
+# Display the plots
+print(plot_female)
+```
+\newpage
+```{r fig-problem1-male, echo=FALSE, fig.cap="The percentage of male participants' choices within each condition in problem 1."}
+# Create plots for 'Female'
+plot_male <- create_gender_plot("Male", data)
+# Display the plots
+print(plot_male)
+```
+\newpage
+
+### Problem 2:
+
+```{r echo=FALSE}
+# Translate 'gênero' to English and remove rows with NA choices
+data2 <- data %>%
+  mutate(gênero = recode(gênero, 'Mulher' = 'Female', 'Homem' = 'Male')) %>%
+  filter(!is.na(`A casa_1`), !is.na(`A casa_2`), !is.na(`A casa_3`))
+
+# Reshape the data for plotting
+Prob2_data <- data2 %>%
+  pivot_longer(cols = c(`A casa_1`, `A casa_2`, `A casa_3`),
+               names_to = "Seller_Rank",
+               values_to = "Choice") %>%
+  mutate(Seller_Rank = recode(Seller_Rank,
+                               `A casa_1` = "Andre",
+                               `A casa_2` = "Bento",
+                               `A casa_3` = "Marcelo"),
+         Choice = factor(Choice, levels = c(1, 2, 3), labels = c("First Choice", "Second Choice", "Third Choice"))) %>%
+  group_by(gênero, Seller_Rank, Choice) %>%
+  summarise(Count = n(), .groups = 'drop')
+
+# Calculate the percentages without NA values
+Prob2_data <- Prob2_data %>%
+  group_by(gênero, Choice) %>%
+  mutate(Percentage = Count / sum(Count) * 100) %>%
+  ungroup()
+
+# Function to create plot for each gender
+create_plot <- function(gender, data) {
+  gender_data <- data %>%
+    filter(gênero == gender)
+
+  # Plot
+  ggplot(gender_data, aes(x = Choice, y = Percentage, fill = Seller_Rank)) +
+    geom_bar(stat = "identity", position = position_dodge(), color = "black") +
+    scale_fill_brewer(palette = "Pastel1") +
+    labs(
+      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 2"),
+      x = "Rank",
+      y = "Percentage",
+      fill = "Seller"
+    ) +
+    theme(legend.position = "bottom") +
+    ylim(0, 100)
+}
+```
+
+```{r fig-problem2-female, echo=FALSE, fig.cap="The percentage of female participants' choices ranking each seller in problem 2"}
+# Create plots for 'Female'
+plot_female2 <- create_plot("Female", Prob2_data)
+# Display the plots
+print(plot_female2)
+```
+\newpage
+```{r fig-problem2-male, echo=FALSE, fig.cap="The percentage of male participants' choices ranking each seller in problem 2"}
+# Create plots for 'Female'
+plot_male2 <- create_plot("Male", Prob2_data)
+# Display the plots
+print(plot_male2)
+```
+\newpage
+### Problem 3
+
+```{r echo=FALSE}
+# Translate the terms to English and filter out NA values selectively
+data3 <- data %>%
+  mutate(
+    across(
+      .cols = c("poltrona_venda_reais", "poltrona_compra_reai", "poltrona_venda_porce"),
+      .fns = ~ case_when(
+        . == "Menos suscetível" ~ "Less",
+        . == "Mais suscetível" ~ "More",
+        . == "Igual" ~ "Same",
+        TRUE ~ NA_character_
+      )
+    ),
+    gênero = recode(gênero, 'Mulher' = 'Female', 'Homem' = 'Male')
+  )
+
+# Reshape the data for plotting
+Prob3_data <- data3 %>%
+  pivot_longer(
+    cols = c("poltrona_venda_reais", "poltrona_compra_reai", "poltrona_venda_porce"),
+    names_to = "Condition",
+    values_to = "Likelihood"
+  ) %>%
+  filter(!is.na(Likelihood)) %>%
+  mutate(
+    Decision = case_when(
+      str_detect(Condition, "compra") ~ "Buy",
+      str_detect(Condition, "venda") ~ "Sell"
+    ),
+    Likelihood = factor(Likelihood, levels = c("More", "Same", "Less"))
+  )
+
+# Counting and percentage calculation
+Prob3_data <- Prob3_data %>%
+  count(gênero, Decision, Likelihood) %>%
+  group_by(gênero, Decision) %>%
+  mutate(Percentage = n / sum(n) * 100) %>%
+  ungroup()
+
+# Function to create plot for each gender
+create_plot <- function(gender, data) {
+  gender_data <- data %>%
+    filter(gênero == gender)
+  # Plot
+  ggplot(gender_data, aes(x = Decision, y = Percentage, fill = Likelihood)) +
+    geom_bar(stat = "identity", position = position_dodge(), color = "black") +
+    scale_fill_brewer(palette = "Pastel1") +
+    labs(
+      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment"),
+      x = "Decision",
+      y = "Percentage",
+      fill = "Likelihood"
+    ) +
+    theme(legend.position = "bottom") +
+    ylim(0, 100)
+}
+```
+
+```{r fig-problem3-female, echo=FALSE, fig.cap="The percentage of female participants' choices (more, same, less) for both 'buy' and 'sell' conditions in problem 3"}
+# Create plots for 'Female'
+plot_female3 <- create_plot("Female", Prob3_data)
+# Display the plots
+print(plot_female3)
+```
+\newpage
+```{r fig-problem3-male, echo=FALSE, fig.cap="The percentage of male participants' choices (more, same, less) for both 'buy' and 'sell' conditions in problem 3"}
+# Create plots for 'Female'
+plot_male3 <- create_plot("Male", Prob3_data)
+# Display the plots
+print(plot_male3)
+```
+\newpage
+### Problem 4
+```{r echo=FALSE}
 

### 2024-02-13 scripts/01-cleanup-data.R

@@ -11,7 +11,7 @@ library(here)
 # These variables are used to store the file path to get the file before data cleaning
 # and save the file after data cleaning
 input_file_path <- here("inputs", "data", "money_data_raw.xlsx")
-output_file_path <- here("outputs", "data", "cleaned_money_data_raw.csv")
+output_file_path <- here("outputs", "data", "cleaned_money_data.csv")
 
 # Read the raw dataset
 raw_data <- readxl::read_excel(input_file_path)

### 2024-02-13 outputs/paper/paper.qmd
added 2 new plots

@@
     labs(
-      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment"),
+      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 3"),
       x = "Decision",
@@
 ```{r echo=FALSE}
+data4 <- data %>%
+  mutate(gênero = recode(gênero, 'Mulher' = 'Female', 'Homem' = 'Male'))
 
+# Pivot the data to long format, ensure columns start with 'contrato'
+long_data <- data4 %>%
+  pivot_longer(
+    cols = starts_with("contrato"), # This assumes column names start with 'contrato'
+    names_to = "Contract",
+    values_to = "Choice",
+    values_drop_na = TRUE
+  ) %>%
+  mutate(
+    Term = case_when(
+      Contract == "contrato_AB" ~ "Real Terms",
+      Contract == "contrato_CD" ~ "Nominal Terms",
+      Contract == "contrato_EF" ~ "Neutral Terms"
+    ),
+    Choice = case_when(
+      Choice %in% c("A", "C", "E") ~ "Risky",
+      Choice %in% c("B", "D", "F") ~ "Riskless"
+    ),
+    Term = fct_relevel(Term, "Real Terms", "Nominal Terms", "Neutral Terms") # Order the terms
+  ) %>%
+  drop_na(Choice) # Drop NA values to avoid them being plotted
+
+# Calculate the counts and percentages
+data_counts <- long_data %>%
+  count(gênero, Term, Choice) %>%
+  group_by(gênero, Term) %>%
+  mutate(Percentage = n / sum(n) * 100)
+
+# Plotting function
+create_plot <- function(gender, data) {
+  gender_data <- data %>%
+    filter(gênero == gender)
+
+  ggplot(gender_data, aes(x = Term, y = Percentage, fill = Choice)) +
+    geom_bar(stat = "identity", position = position_dodge()) +
+    scale_fill_brewer(palette = "Pastel1") +
+    labs(
+      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 4"),
+      x = "Terms",
+      y = "Percentage",
+      fill = "Choice"
+    ) +
+    theme_minimal() +
+    ylim(0, 100)
+}
+```
+
+```{r fig-problem4-female, echo=FALSE, fig.cap="The percentage of female participants' choices of contract types across frames(real, nominal and neutral) in problem 4"}
+# Create plots for 'Female'
+plot_female4 <- create_plot("Female", data_counts)
+# Display the plots
+print(plot_female4)
+```
+\newpage
+```{r fig-problem4-male, echo=FALSE, fig.cap="The percentage of male participants' choices of contract types across frames(real, nominal and neutral) in problem 4"}
+# Create plots for 'Male'
+plot_male4 <- create_plot("Male", data_counts)
+# Display the plots
+print(plot_male4)
 ```

### 2024-02-13 outputs/paper/paper.qmd
added writting

--- 2024-02-13 outputs/paper/paper.qmd
@@
 # Un-comment these lines for missing packages
-# install.packages("lubridate")
 # install.packages("dplyr")
@@
 # install.packages("tidyverse")
-# install.packages("readxl")
 
 ## Import nessasay libraries
-library(readxl)
 library(ggplot2)
@@
 
+Data cleaning is a critical step in ensuring the accuracy and reliability of the analysis.
+The detailed procedure and the R script used for data cleaning are available in `scripts/01_cleanup_data.R`.
+The script elucidates the steps taken to refine the dataset by filtering out incomplete records and unnecessary columns for this study.
+The steps are: 1.
+Remove the first row in the dataset, since it is used to store the description to the column name.
+2.
+Remove unnecessary columns for this study, by only keep the gender and responses columns.
+3.
+Remove all gender rows with 'na' since this study is focusing on the behavior for money illusion for male and female participants.
+The cleaned dataset is conveniently saved at `outputs/data/cleaned_money_data.csv`, ready for in-depth analysis.
+
 ### Data Sample
@@
 ### Problem 1:
+
+**Hypothetical Analysis:**
+Gender Perspectives on Economic Decisions: The graph suggests that men favored "Carolina" in economic terms and "Maria" in job attractiveness.
+This could hypothetically indicate that men associate the concept of "Carolina" with economic stability and "Maria" with professional opportunities.
+Analyzing this alongside gender could reveal whether women make similar associations or have a contrasting view.
+
 ```{r echo=FALSE}
@@
     geom_bar(stat = "identity", position = position_dodge(), color = "black") +
-    scale_fill_brewer(palette = "Pastel1") +
     labs(
@@
 ```
-\newpage
+Observations from @fig-problem1-female for female participants' choices:
+
+Economic Terms: A significant majority of female participants chose "Carolina" over "Maria" in economic terms.
+This choice distribution is similar to that of the male participants, suggesting a consensus across genders regarding economic choices tied to "Carolina".
+
+Happiness: Female participants seem evenly split between "Carolina" and "Maria" when it comes to happiness, which differs from male participants, who showed a slight preference for "Maria" in this condition.
+This could suggest that women see both "Carolina" and "Maria" as equally viable options for emotional fulfillment or that happiness is not as strongly associated with either choice as it is with economic terms.
+
+Job Attractiveness: The choices for job attractiveness among female participants are also evenly distributed between "Carolina" and "Maria", whereas male participants had a preference for "Maria".
+This could imply that for women, the qualities or opportunities represented by "Carolina" and "Maria" are equally attractive in a professional setting.
+
 ```{r fig-problem1-male, echo=FALSE, fig.cap="The percentage of male participants' choices within each condition in problem 1."}
@@
 ```
+Observations from @fig-problem1-male for male participants' choices:
+
+Economic Terms: A significant majority of male participants chose "Carolina" over "Maria" in economic terms.
+This indicates a strong preference for the economic implications associated with "Carolina" among male participants, suggesting they may perceive "Carolina" as a more stable or profitable economic choice.
+
+Happiness: The male participants' choices for happiness are nearly evenly split, with a slight preference for "Carolina." This distribution shows that men do not strongly associate either "Carolina" or "Maria" with happiness or that they see both options as similarly capable of providing emotional satisfaction.
+
+Job Attractiveness: Male participants displayed a clear preference for "Maria" in terms of job attractiveness.
+This could suggest that the attributes or opportunities associated with "Maria" resonate more with men when considering the attractiveness of a job or career path.
+
+**Gender Comparison Analysis:**
+Economic Rationality: Both genders show a strong preference for "Carolina" in economic terms, which might suggest that "Carolina" represents a more financially beneficial or stable option.
+This similarity indicates that both men and women may prioritize financial stability in their decision-making processes.
+
+Emotional Considerations: The contrast in happiness choices between genders is subtle but present.
+Men's slight preference for "Maria" might suggest that they associate "Maria" with emotional well-being slightly more than women do.
+However, women's even split could indicate a balanced view or a lesser degree of differentiation between "Carolina" and "Maria" in terms of happiness.
+
+Professional Preferences: The difference in job attractiveness choices is more pronounced, with men preferring "Maria" and women showing no clear preference.
+This may suggest that men and women have different criteria for what makes a job attractive or that they value different aspects of a job.
+
+**Hypothetical Narrative:**
+Given these observations, we might theorize that both men and women in this experiment view "Carolina" as the more economically sound choice.
+This could reflect a societal consensus on certain financial principles or values.
+
+In terms of happiness and job attractiveness, women's even split between "Carolina" and "Maria" contrasts with men's preferences, potentially indicating that women have a more holistic approach, valuing multiple aspects equally when it comes to job satisfaction and emotional well-being.
+
+**Conclusion:**
+The data from both genders in the Money Illusion Experiment 1 seems to suggest that while there may be common ground in economic decisions, there are nuanced differences in how happiness and job attractiveness are perceived.
+These differences could be due to various factors, including societal roles, individual experiences, or inherent biases in the experiment design.
+
+It's important to note that these interpretations are speculative and based on limited information.
+In reality, a thorough analysis would require more context about the experiment, including how "Carolina" and "Maria" were presented to the participants and what they represent, as well as a deeper statistical analysis to validate any conclusions drawn.
+Additionally, a more nuanced understanding of "rationality" and "emotion" in economic decisions would be necessary to make more definitive claims about gender differences in financial perspectives.
+
 \newpage
@@
 ### Problem 2:
+
+**Hypothetical Analysis:**
+
+Gender Perspectives on Seller Choices: The graphs for Money Illusion Experiment 2 show distinct patterns in how male and female participants rank sellers—Andre, Bento, and Marcelo.
+Hypothetically, this could indicate that male participants associate Andre with immediate value or appeal, as evidenced by his high ranking as the first choice, while Bento and Marcelo may represent longer-term benefits or stability, which becomes more apparent in the subsequent choices.
+On the other hand, female participants show a strong initial preference for Marcelo, suggesting they may perceive Marcelo as a symbol of immediate trustworthiness or value.
+Bento's consistent middle-ground ranking among females could indicate a perception of balanced or average appeal.
+
+The preference dynamics could be interpreted as men being more likely to revise their initial judgments, while women might be consistent in their preferences.
+Analyzing these choices alongside gender could reveal whether men and women apply different criteria when evaluating the options presented to them, possibly due to differing risk assessments, values, or expectations in economic decisions.
+The shift in preferences for both genders as they move from first to third choice could suggest a complex decision-making process where initial impressions are adjusted upon further reflection or comparison.
 
@@
 ```
-\newpage
+Observations from @fig-problem2-female for female participants' choices:
+First Choice:
+
+Andre appears to be the least favored as the first choice among female participants.
+Bento has a moderate preference as the first choice.
+Marcelo is the most preferred seller for the first choice.
+Second Choice:
+
+Andre sees a significant increase in preference from the first to the second choice.
+Bento is the most selected as the second choice.
+Marcelo's preference drops, making him the least favored for the second choice.
+Third Choice:
+
+Andre is again the least preferred as the third choice.
+Bento's preference decreases compared to the second choice.
+Marcelo's preference increases, making him the most favored for the third choice.
+
 ```{r fig-problem2-male, echo=FALSE, fig.cap="The percentage of male participants' choices ranking each seller in problem 2"}
@@
 ```
+Observations from @fig-problem2-male Male Participants' Choices:
+
+First Choice:
+Andre has the highest preference as the first choice among male participants.
+Bento is the least preferred as the first choice.
+Marcelo has a moderate preference as the first choice.
+
+Second Choice:
+Andre's preference decreases significantly from the first to the second choice.
+Bento is the most preferred as the second choice, showing a substantial increase from the first choice.
+Marcelo's preference remains relatively stable across the first and second choices.
+
+Third Choice:
+Andre has a moderate increase in preference as the third choice.
+Bento's preference drops slightly from the second choice.
+Marcelo sees a significant increase and is the most favored as the third choice.
+
+**Gender Comparison Analysis:**
+First Choice Dynamics:
+
+Male participants show a clear preference for Andre as their first choice, while female participants favor Marcelo.
+This difference could reflect varying criteria or perceptions of value between genders.
+Bento is the least favored first choice by males but holds a moderate preference among females, suggesting different initial impressions based on gender.
+Evolution of Preferences:
+
+Both genders show a shifting pattern in their preferences from the first to the third choice, indicating a reevaluation of the sellers as they move down the rank order.
+
+Andre's stark contrast between the first and subsequent choices in male participants could suggest a reconsideration of initial impressions after comparing all options.
+Consensus on Final Choices:
+
+Marcelo emerges as the most favored third choice for both genders, suggesting a commonality in the eventual perception of value or appeal.
+
+**Hypothetical Narrative:**
+
+The divergent first choices between genders could imply that male and female participants have different priorities or strategies in initial decision-making.
+As the ranking progresses, both genders adjust their preferences, which could suggest a nuanced evaluation process where certain qualities or offers become more or less important as comparison occurs.
+This pattern of preference change might reflect a complex decision-making process influenced by a variety of factors, including risk assessment, perceived value, or even seller presentation.
+
+**Conclusion:**
+
+While male and female participants show different initial preferences, there is a convergence in choices by the third rank, with Marcelo being the favored seller for both.
+This could indicate that while initial assessments may vary between genders, there is potential for a shared consensus to emerge as more information is considered.
+It is important to recognize that these interpretations are based on limited data from the bar graphs provided and the actual reasons behind these choices could be multifaceted and would benefit from further qualitative insights.
+
 \newpage
 ### Problem 3
+
+**Hypothetical Analysis:**
+
+Gender Perspectives on Financial Decisions: The graphs for Money Illusion Experiment 3 display the decision-making tendencies of male and female participants when faced with the option to buy or sell under varying conditions of likelihood ('More', 'Same', 'Less').
+Analyzing this alongside gender can reveal nuanced approaches to market engagement.
+This hypothetical analysis could be pointing to underlying gender differences in economic decision-making, where men might prioritize growth or investment maintenance, and women might prioritize financial security and opportunistic gains.
+However, it's crucial to approach these assumptions critically, as individual decisions are influenced by a range of personal, social, and economic factors beyond gender.
 
@@
     geom_bar(stat = "identity", position = position_dodge(), color = "black") +
-    scale_fill_brewer(palette = "Pastel1") +
     labs(
-      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment"),
+      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 3"),
       x = "Decision",
@@
 ```
-\newpage
+Observations from @fig-problem3-female for female participants' choices:
+
+Buy Decisions: Females show the least likelihood to buy more and a similar inclination to buy less or the same.
+This could indicate a cautious or conservative approach to purchasing decisions, possibly prioritizing stability or risk aversion.
+
+Sell Decisions: The tendency to sell more is considerably higher than to sell less, with selling the same as an intermediate option.
+This pattern might suggest a greater openness to divesting or capitalizing on assets when conditions are favorable, or it could reflect a strategic approach to managing investments.
+
 ```{r fig-problem3-male, echo=FALSE, fig.cap="The percentage of male participants' choices (more, same, less) for both 'buy' and 'sell' conditions in problem 3"}
@@
 ```
+Observations from @fig-problem3-male for male participants' choices:
+
+Buy Decisions: Males show a balanced approach between buying more and the same, with less likelihood to buy less.
+This distribution could imply a more assertive or optimistic strategy toward acquiring assets or a greater confidence in market conditions.
+
+Sell Decisions: There is a strong preference for selling the same, followed by selling more, and the least for selling less.
+This could suggest a preference for maintaining the status quo or a calculated approach to selling, where changes in market conditions are considered but not reacted to hastily.
+
+**Gender Comparison**
+
+Buying Behavior: Females appear more conservative, potentially weighing the risks more heavily, while males seem to demonstrate a readiness to invest, indicating a possible difference in risk tolerance.
+Selling Behavior: Females are more likely to sell more, which might suggest a strategy to capitalize on gains or avoid losses.
+In contrast, males' preference for selling the same amount could indicate a long-term investment strategy or a less reactive approach to market fluctuations.
+
+**Conclusion:**
+
+The observed differences in the buying and selling behaviors of male and female participants in Money Illusion Experiment 3 may reflect underlying gender-specific financial strategies or risk preferences.
+While females may exhibit cautious purchasing behavior and a proactive selling stance, males seem to lean toward balanced buying and less reactive selling.
+These insights, while hypothetical, could inform further investigation into gender-based economic decision-making patterns.
+It's important to acknowledge that these interpretations are speculative and that actual decision-making processes are complex and influenced by a myriad of factors beyond gender.
+
 \newpage
 ### Problem 4
+
+**Hypothetical Analysis:**
+Gender Perspectives on Financial Risk Decisions: The graphs for Money Illusion Experiment 4 reveal the choices of male and female participants regarding different contract types characterized as riskless and risky across real, nominal, and neutral terms.
+
 ```{r echo=FALSE}
+data4 <- data %>%
+  mutate(gênero = recode(gênero, 'Mulher' = 'Female', 'Homem' = 'Male'))
 
+# Pivot the data to long format, ensure columns start with 'contrato'
+long_data <- data4 %>%
+  pivot_longer(
+    cols = starts_with("contrato"), # This assumes column names start with 'contrato'
+    names_to = "Contract",
+    values_to = "Choice",
+    values_drop_na = TRUE
+  ) %>%
+  mutate(
+    Term = case_when(
+      Contract == "contrato_AB" ~ "Real Terms",
+      Contract == "contrato_CD" ~ "Nominal Terms",
+      Contract == "contrato_EF" ~ "Neutral Terms"
+    ),
+    Choice = case_when(
+      Choice %in% c("A", "C", "E") ~ "Risky",
+      Choice %in% c("B", "D", "F") ~ "Riskless"
+    ),
+    Term = fct_relevel(Term, "Real Terms", "Nominal Terms", "Neutral Terms") # Order the terms
+  ) %>%
+  drop_na(Choice) # Drop NA values to avoid them being plotted
+
+# Calculate the counts and percentages
+data_counts <- long_data %>%
+  count(gênero, Term, Choice) %>%
+  group_by(gênero, Term) %>%
+  mutate(Percentage = n / sum(n) * 100)
+
+# Plotting function
+create_plot <- function(gender, data) {
+  gender_data <- data %>%
+    filter(gênero == gender)
+
+  ggplot(gender_data, aes(x = Term, y = Percentage, fill = Choice)) +
+    geom_bar(stat = "identity", position = position_dodge()) +
+    labs(
+      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 4"),
+      x = "Terms",
+      y = "Percentage",
+      fill = "Choice"
+    ) +
+    theme_minimal() +
+    ylim(0, 100)
+}
 ```
+
+```{r fig-problem4-female, echo=FALSE, fig.cap="The percentage of female participants' choices of contract types across frames(real, nominal and neutral) in problem 4"}
+# Create plots for 'Female'
+plot_female4 <- create_plot("Female", data_counts)
+# Display the plots
+print(plot_female4)
+```
+Observations from @fig-question4-female for female participants' choices:
+
+Real Terms: Females show a preference for riskless contracts, potentially indicating a perception of real terms as more tangible and, thus, preferring security in transactions that are adjusted for inflation or reflect actual purchasing power.
+
+Nominal Terms: A slight preference for riskless contracts over risky ones in nominal terms could suggest a cautious approach towards transactions that are not adjusted for inflation, reflecting a concern for potential value loss over time.
+
+Neutral Terms: The distribution is more balanced, but still, riskless contracts are slightly preferred, which might indicate a general tendency towards caution regardless of the framing of terms.
+
+```{r fig-problem4-male, echo=FALSE, fig.cap="The percentage of male participants' choices of contract types across frames(real, nominal and neutral) in problem 4"}
+# Create plots for 'Male'
+plot_male4 <- create_plot("Male", data_counts)
+# Display the plots
+print(plot_male4)
+```
+Observations from @fig-question4-male for male participants' choices:
+
+Real Terms: Males show an overwhelming preference for riskless contracts in real terms, possibly valuing the certainty of returns that account for inflation and maintain purchasing power.
+
+Nominal Terms: The preference shifts towards risky contracts, implying that men might be more willing to engage in speculative transactions when dealing with nominal values that do not account for inflation.
+
+Neutral Terms: There is a nearly even split, with a slight lean towards riskless contracts, suggesting that without specific framing, men might default to a more balanced risk approach.
+
+**Gender Comparison:**
+
+Risk Preferences in Real Terms: Both genders exhibit a strong preference for riskless contracts, possibly due to the direct impact of inflation-adjusted transactions on real-world purchasing power.
+
+Risk Preferences in Nominal Terms: A stark difference is observed; women remain cautious, whereas men become risk-takers, which could imply a gender-based divergence in responses to economic scenarios where inflation or value erosion is a factor.
+
+Risk Preferences in Neutral Terms: The slight preference for riskless contracts among both genders indicates a baseline aversion to risk when the terms are not clearly defined or when the framing is neutral.
+
+**Conclusion:**
+
+The data from Money Illusion Experiment 4 suggests that both men and women tend to prefer riskless contracts, especially in real terms, indicating a common desire for security in financially tangible scenarios.
+However, when the framing shifts to nominal terms, gender differences emerge, with men displaying a higher tolerance for risk.
+These hypothetical observations could reflect underlying gender differences in financial risk perception and economic decision-making.
+However, it is critical to consider these insights within the broader context of individual financial behavior, which is influenced by various personal, cultural, and situational factors beyond gender.
 
@@
 
+## Apenndix
+
+### Rough Sketch about Brainstorming
+
+For a visual depiction of the brainstorming process and the initial ideas that shaped this study, please refer to the document located at `inputs/misc/Plan-Sketch.pdf`.
+This sketch includes preliminary thoughts on the data structure and one potential approach to address the research questions.
+
+### Data Simulation
+
+The simulated dataset, designed to mirror the structure of the actual "Money Illusion" dataset, can be found at `scripts/00-simulate-data_data.R`.
+This script meticulously generates a dataset of 100 hypothetical delay instances.
+
+### Download Data from Open Science Framework
+
+Interested researchers can access the original dataset from the Brazilian researchers for further analysis or replication studies at the following URL: https://osf.io/48pqu/
+
+### Data Cleaning Process
+
+Data cleaning is a critical step in ensuring the accuracy and reliability of the analysis.
+The detailed procedure and the R script used for data cleaning are available in `scripts/01_cleanup_data.R`.
+The script elucidates the steps taken to refine the dataset by filtering out incomplete records and unnecessary columns for this study.
+The steps are: 1.
+Remove the first row in the dataset, since it is used to store the description to the column name.
+2.
+Remove unnecessary columns for this study, by only keep the gender and responses columns.
+3.
+Remove all gender rows with 'na' since this study is focusing on the behavior for money illusion for male and female participants.
+The cleaned dataset is conveniently saved at `outputs/data/cleaned_money_data.csv`, ready for in-depth analysis.
+
+### Data Set Validity Testing
+
+To affirm the integrity and consistency of the cleaned dataset, a series of validation tests are performed using the script `scripts/03-test-data-validity.R`.
+This script performs three crucial checks to ensure the data set's accuracy and consistency:
+
 ## Reference

### 2024-02-14 outputs/paper/paper.qmd
modified introduction

@@
 The results indicate that participants' tend to choose financially advantages opportunities which  influenced by the framing of terms (real, nominal, or neutral).
+We invetigate the money illusion across gender , we found that male is more rational than female in different aspects of money illusion.
 After we replicate across all four scenarios, the findings suggest that the money illusion effect  transcend cultural boundaries, supported by replication within a different background of cultural context."
@@
 
+From a stereotypical perspective, women is more emotional than men in the aspect of luxury consumptions, despite similar functional value to non-luxury brands, luxury brands command higher prices, especially among female consumers[@stokburger2013luxury].
+
 For decades, economists have debated whether the money illusion is real or, more generally, whether there are irrational influences in economic transactions.
@@
 
-In this paper, our hypothesis are across all four problems: in problem 1, individuals inclined to perceive wage increases significantly in real term even if it is small in nominal terms; In problem 2, individuals will evaluate house deals based on nominal gains rather than real gains; In problem 3, participants will be less likely to purchase new items rather than second hand items when prices increase nominally; In problem 4, individuals might prefer riskier contracts in real terms over safer options presented in nominal terms.
+The original paper has 4 research problems: in problem 1, individuals inclined to perceive wage increases significantly in real term even if it is small in nominal terms; In problem 2, individuals will evaluate house deals based on nominal gains rather than real gains; In problem 3, participants will be less likely to purchase new items rather than second hand items when prices increase nominally; In problem 4, individuals might prefer riskier contracts in real terms over safer options presented in nominal terms.
+In this paper, we will focus on the relationship between gender and money illusion in the four research problems mentioned above.
 
@@
 ```
-Observations from @fig-question4-female for female participants' choices:
+Observations from @fig-problem4-female for female participants' choices:
 
@@
 ```
-Observations from @fig-question4-male for male participants' choices:
+Observations from @fig-problem4-male for male participants' choices:
 

### 2024-02-15 outputs/paper/paper.qmd
added new scripts

@@
 ---
-title: "Replicating the \"Money Illusion\" Effect: Exploring Gender Influences within a Brazilian Sample"
+title: "Gender Dynamics in Financial Decision-Making: Unveiling the Money Illusion Effect in Brazil"
 title-block-banner: true
-abstract: "Money illusion as the tendency to overlook the impact of inflation which focusing on nominal values identified by Shafir, Diamond, and Tversky (1997).
-This study reproduce four scenarios from research where participants face financial decisions influenced by money illusion in various situations such as earnings, transactions, and contracts,under the background of Brazilian context, where in various situations such as transactions, transactions and earnings that participants face financial decisions influenced by money illusion.
-The cross-sectional and pre-registered research is based on 372 Brazilian participants in mobile phones or computers by using chi-square tests assessed money illusion.
-The results indicate that participants' tend to choose financially advantages opportunities which  influenced by the framing of terms (real, nominal, or neutral).
-We invetigate the money illusion across gender , we found that male is more rational than female in different aspects of money illusion.
-After we replicate across all four scenarios, the findings suggest that the money illusion effect  transcend cultural boundaries, supported by replication within a different background of cultural context."
-thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Student-Replication-For-Money-Illusion.git"
+abstract: "Money illusion is a cognitive bias where individuals focus on nominal rather than real values, a concept initially highlighted by Shafir, Diamond, and Tversky (1997).
+In this study, we replicated four scenarios from their research within the Brazilian context, involving 372 participants making financial decisions impacted by money illusion in contexts of earnings and transactions.
+Through our analysis, we found that decision-making was significantly influenced by the framing of information, with notable differences in rationality between genders.
+Our findings highlight that the effects of money illusion may also vary by gender, showcasing distinct patterns of financial behavior between males and females."
+thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git; Replication on Social Science Reproduction platform available at: "
 author: "Terry Tu, Jingyi Shen, Yaning Jin "
@@
 ```
+
 ```{r table2, echo=FALSE}
@@
 
-### Problem 1:
+### Problem 1: Gender and Preference in Economic Decision-Making
 
@@
     labs(
-         title = paste("Choices Distribution for", gender, "in Money Illusion Experiment 1"),
          x = "Condition",
@@
 **Gender Comparison Analysis:**
+
 Economic Rationality: Both genders show a strong preference for "Carolina" in economic terms, which might suggest that "Carolina" represents a more financially beneficial or stable option.
@@
 
-**Hypothetical Narrative:**
-Given these observations, we might theorize that both men and women in this experiment view "Carolina" as the more economically sound choice.
-This could reflect a societal consensus on certain financial principles or values.
-
-In terms of happiness and job attractiveness, women's even split between "Carolina" and "Maria" contrasts with men's preferences, potentially indicating that women have a more holistic approach, valuing multiple aspects equally when it comes to job satisfaction and emotional well-being.
-
-**Conclusion:**
-The data from both genders in the Money Illusion Experiment 1 seems to suggest that while there may be common ground in economic decisions, there are nuanced differences in how happiness and job attractiveness are perceived.
-These differences could be due to various factors, including societal roles, individual experiences, or inherent biases in the experiment design.
-
-It's important to note that these interpretations are speculative and based on limited information.
-In reality, a thorough analysis would require more context about the experiment, including how "Carolina" and "Maria" were presented to the participants and what they represent, as well as a deeper statistical analysis to validate any conclusions drawn.
-Additionally, a more nuanced understanding of "rationality" and "emotion" in economic decisions would be necessary to make more definitive claims about gender differences in financial perspectives.
-
 \newpage
-
-### Problem 2:
+### Problem 2: Gender and Seller Choice
 
@@
     labs(
-      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 2"),
       x = "Rank",
@@
 **Gender Comparison Analysis:**
+
 First Choice Dynamics:
@@
 
-**Hypothetical Narrative:**
-
-The divergent first choices between genders could imply that male and female participants have different priorities or strategies in initial decision-making.
-As the ranking progresses, both genders adjust their preferences, which could suggest a nuanced evaluation process where certain qualities or offers become more or less important as comparison occurs.
-This pattern of preference change might reflect a complex decision-making process influenced by a variety of factors, including risk assessment, perceived value, or even seller presentation.
-
-**Conclusion:**
-
-While male and female participants show different initial preferences, there is a convergence in choices by the third rank, with Marcelo being the favored seller for both.
-This could indicate that while initial assessments may vary between genders, there is potential for a shared consensus to emerge as more information is considered.
-It is important to recognize that these interpretations are based on limited data from the bar graphs provided and the actual reasons behind these choices could be multifaceted and would benefit from further qualitative insights.
-
 \newpage
-### Problem 3
+### Problem 3: Gender and Market Participation Decisions
 
@@
     labs(
-      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 3"),
       x = "Decision",
@@
 Buying Behavior: Females appear more conservative, potentially weighing the risks more heavily, while males seem to demonstrate a readiness to invest, indicating a possible difference in risk tolerance.
+
 Selling Behavior: Females are more likely to sell more, which might suggest a strategy to capitalize on gains or avoid losses.
@@
 
-**Conclusion:**
-
-The observed differences in the buying and selling behaviors of male and female participants in Money Illusion Experiment 3 may reflect underlying gender-specific financial strategies or risk preferences.
-While females may exhibit cautious purchasing behavior and a proactive selling stance, males seem to lean toward balanced buying and less reactive selling.
-These insights, while hypothetical, could inform further investigation into gender-based economic decision-making patterns.
-It's important to acknowledge that these interpretations are speculative and that actual decision-making processes are complex and influenced by a myriad of factors beyond gender.
-
 \newpage
-### Problem 4
+### Problem 4: Gender and Financial Risk Decision-Making
 
@@
     labs(
-      title = paste("Choice Distribution for", gender, "in Money Illusion Experiment 4"),
       x = "Terms",
@@
 
-**Conclusion:**
-
-The data from Money Illusion Experiment 4 suggests that both men and women tend to prefer riskless contracts, especially in real terms, indicating a common desire for security in financially tangible scenarios.
-However, when the framing shifts to nominal terms, gender differences emerge, with men displaying a higher tolerance for risk.
-These hypothetical observations could reflect underlying gender differences in financial risk perception and economic decision-making.
-However, it is critical to consider these insights within the broader context of individual financial behavior, which is influenced by various personal, cultural, and situational factors beyond gender.
-
-## Conclusion
+## Discussion
 

### 2024-02-15 scripts/01-cleanup-data.R

@@ -1,27 +1,29 @@
-# Load necessary libraries
-# install.packages("dplyr")
-# install.packages("readxl")
-# install.packages("here")
+# install necessary libraries
+install.packages("dplyr")
+install.packages("readxl")
+install.packages("here")
 
+# Load necessary libraries
 library(readxl)
 library(dplyr)
 library(here)
 
 # Use the `here` function to specify file paths relative to the project root
-# These variables are used to store the file path to get the file before data cleaning
-# and save the file after data cleaning
+# These variables are used to store the file path to get the file before 
+# data cleaning and save the file after data cleaning
 input_file_path <- here("inputs", "data", "money_data_raw.xlsx")
 output_file_path <- here("outputs", "data", "cleaned_money_data.csv")
 
-# Read the raw dataset
+# Read the raw data-set
 raw_data <- readxl::read_excel(input_file_path)
 
-# Remove the first row from the dataset
+# Remove the first row from the data-set
+# This row is used to store the description about the column name
 cleaned_data <- raw_data %>% 
   slice(-1)
 
-# Remove unessasay columns for this study
-# We only want the gender and choices columns
+# Remove unnecessary columns for this study
+# We only want the gender column and response choices columns
 cleaned_data <- cleaned_data %>%
   select(
     -idade, 
@@ -41,7 +43,7 @@ cleaned_data <- cleaned_data %>%
 
 # Remove rows where gender is NA
 cleaned_data <- cleaned_data %>%
-  filter(!is.na(gênero))
+  filter(!is.na(gênero) & gênero != 'Outro')
 
-# Optionally, save the cleaned dataset to a CSV file
+# Save the cleaned dataset to a CSV file
 write.csv(cleaned_data, output_file_path, row.names = FALSE)

### 2024-02-15 scripts/02-test-data-validity.R

@@ -1,0 +1,69 @@
+# Install necessary packages
+# install.packages("dplyr")
+# install.packages("readr")
+# install.packages("here")
+
+# Load necessary packages
+library(readr)
+library(dplyr)
+library(here)
+
+# Load the cleaned money illusion data to variable 'data'
+file_path <- here("outputs", "data", "cleaned_money_data.csv")
+data <- read_csv(file_path)
+
+# Below are the 7 tests for the cleaned dataset, 
+# after running them we expected to get TRUE for all test cases
+
+# Test 1: No missing value for gender column
+# No NA in the 'gênero' column
+test_gênero_NA <- all(!is.na(data$gênero))
+
+
+# Test 2: Total entries are more than 300
+test_entries_over_300 <- nrow(data) > 300
+
+
+# Test 3: Gender only contains male or female 
+# 'gênero' column contains only 'Mulher' and 'Homem'
+test_gênero_values <- all(data$gênero %in% c('Mulher', 'Homem'))
+
+
+# Test 4: Testing question 1 response only contain expected values
+# "economicam", "felicidade", "atratividade_trab" columns only have values 'Carolina', 'Maria', or NA
+test_specific_values <- all(sapply(data[c("economicam", "felicidade", "atratividade_trab")], function(x) {
+  all(x %in% c('Carolina', 'Maria', NA))
+}))
+
+
+# Test 5:Testing question 2 response only contain expected values 
+# Columns have values 'Igual', 'Menos suscetível', or NA
+test_casa_values <- all(sapply(data[c("A casa_1", "A casa_2", "A casa_3")], function(x) {
+  all(x %in% c(1, 2, 3, NA))
+}))
+print(paste("Test 5 - Casa columns contain only 1, 2, 3, or NA:", test_casa_values))
+
+
+# Test 6: Testing question 3 response only contain expected values 
+# Columns "A casa_1", "A casa_2", "A casa_3" contain only values 1, 2, 3, or NA
+test_poltrona_values <- all(sapply(data[c("poltrona_venda_reais", "poltrona_compra_reai", "poltrona_venda_porce")], function(x) {
+  all(x %in% c('Igual', 'Menos suscetível', 'Mais suscetível', NA))
+}))
+
+
+# Test 7: 
+# "contrato_AB" contains only "A", "B", or NA; "contrato_CD" contains only "C", "D", or NA; "contrato_EF" contains only "E", "F", or NA
[…]

### 2024-02-15 outputs/paper/paper.qmd
fix issue

@@
 ```{r setup, include=FALSE, message=FALSE}
-# Un-comment these lines for missing packages
+# un-comment to install all required packages
 # install.packages("dplyr")
@@
 
-## Import nessasay libraries
+## Import necessary libraries
 library(ggplot2)
@@
 library(readr)
-knitr::opts_chunk$set(echo = FALSE)
 ```
 
+\newpage
 ## Introduction

### 2024-02-15 outputs/paper/paper.qmd
fixed new issues

@@
 toc: true
-toc-depth: 2
+toc-depth: 1
 number-sections: true
@@
 
-\newpage
 ## Introduction
@@
 These packages include ggplot2 [@rGgplot2] for creating advanced graphics, dplyr [@rDplyr] for data manipulation, readr [@rReadr] for its robust data reading functionalities, here [@R-here] is used to avoid file path issue, and knitr [@rKnitr] for dynamic report generation.
-
-### Data Cleaning
-
-Data cleaning is a critical step in ensuring the accuracy and reliability of the analysis.
-The detailed procedure and the R script used for data cleaning are available in `scripts/01_cleanup_data.R`.
-The script elucidates the steps taken to refine the dataset by filtering out incomplete records and unnecessary columns for this study.
-The steps are: 1.
-Remove the first row in the dataset, since it is used to store the description to the column name.
-2.
-Remove unnecessary columns for this study, by only keep the gender and responses columns.
-3.
-Remove all gender rows with 'na' since this study is focusing on the behavior for money illusion for male and female participants.
-The cleaned dataset is conveniently saved at `outputs/data/cleaned_money_data.csv`, ready for in-depth analysis.
-
-### Data Sample
-
-```{r table1, echo=FALSE}
-selected_data <- data %>%
-  select(1:2, (ncol(data)-2):ncol(data))
-
-knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Money Illusion Data for Question 1",
-             format = "markdown")
-```
-
-```{r table2, echo=FALSE}
-selected_data <- data %>%
-  select(1:2, 12:14)
-
-knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Money Illusion Data for Question 2",
-             format = "markdown")
-```
-
-```{r table3, echo=FALSE}
-selected_data <- data %>%
-  select(1:2, 7:9)
-
-knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Money Illusion Data for Question 3",
-             format = "markdown")
-```
-
-```{r table4, echo=FALSE}
-selected_data <- data %>%
-  select(1:5)
-
-knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Money Illusion Data for Question 4",
-             format = "markdown")
-```
 
@@
     across(
-      .cols = c("poltrona_venda_reais", "poltrona_compra_reai", "poltrona_venda_porce"),
+      .cols = c("poltrona_venda_reais", "poltrona_compra_reai"),
       .fns = ~ case_when(
@@
   pivot_longer(
-    cols = c("poltrona_venda_reais", "poltrona_compra_reai", "poltrona_venda_porce"),
+    cols = c("poltrona_venda_reais", "poltrona_compra_reai"),
     names_to = "Condition",
@@
 
+### Findings
+
+The first experiment focused on exploring how gender affects individuals' decision-making preferences when faced with economic terms and job attractiveness choices.
+The analysis showed that both men and women agreed on their choices regarding economic terms, generally preferring "Carolina," which may reflect a common concern for economic stability across genders.
+However, differences between genders became evident in terms of job attractiveness, with men preferring "Maria," suggesting they have different evaluations of career opportunities and potential for development compared to women.
+The second experiment examined how men and women make choices based on different characteristics of sellers.
+The results indicated that men and women initially preferred different sellers, with men choosing Andre and women choosing Marcelo.
+This finding may reflect different strategies and priorities in economic decision-making between genders.
+As the choices progressed, preferences for sellers converged, especially in the final choice, where Marcelo became the most popular seller.
+The third experiment focused on how gender affects buying and selling decisions, especially under different probability conditions.
+It was observed that women showed a lower likelihood in purchasing decisions and a greater tendency to increase sales, possibly indicating a cautious attitude towards buying and an active strategy towards selling.
+In contrast, men exhibited a more balanced approach to both buying and selling decisions, suggesting a preference for maintaining the status quo rather than making radical adjustments in changing market conditions.
+The fourth experiment delved into how gender influences individual preferences for different types of contracts (risky and risk-free) and different economic terms (real, nominal, neutral).
+Results showed that both men and women preferred risk-free contracts when it came to contracts adjusted for real terms, possibly indicating a common preference to protect purchasing power against inflation.
+However, under nominal terms, men were relatively more inclined to choose risky contracts, revealing a willingness to take risks for higher returns without inflation adjustment.
+
+### Another Understanding of the World
+
+The results from the first experiment further revealed the impact of gender perspectives on preferences for economic stability and career development.
+Specifically, the even distribution of choices among women regarding job attractiveness may indicate they consider a more diverse set of factors in career choices, including but not limited to economic benefits, perhaps placing more emphasis on job satisfaction and other aspects of career development.
+The dynamic change in gender decision-making observed in the second experiment suggests significant gender differences in initial choices, which may diminish as more information is processed.
+This may illustrate a complex evaluation process individuals undergo before making final economic decisions, where initial impressions may be revised.
+The third experiment's results further reinforced our understanding of gender differences in economic risk assessment.
+Women's more conservative buying behavior and more aggressive selling tendency may reflect their strategy of balancing financial security and opportunities.
+Men's balanced buying and selling behavior may represent a more robust long-term investment perspective.
+The findings of the fourth experiment further emphasized differences in financial risk tolerance between genders.
+Particularly under nominal terms, men's higher risk preference may reflect a pursuit of potential high returns, while women's conservative choices may more reflect a focus on capital preservation.
+These differences are significant for understanding how gender affects investment decisions and financial planning.
+Overall, these four experiments have taught us that gender plays a complex and multidimensional role in economic decision-making.
+Gender not only influences individuals' views on economic stability, career opportunities, market behavior, and risk preferences but also affects the processing of information and the formation of final choices during the decision-making process.
+
+### Limitations of the Study:
+
+The first experiment provided insights into gender differences in economic decision-making but also had limitations.
+For example, it might not have captured all relevant factors influencing economic decisions, such as individuals' economic background, education level, and expectations of future economic conditions.
+Moreover, the experimental design might have been too simplistic to fully reflect the complexity of real-life decision-making processes.
+Despite the second experiment offering insights into how gender affects preferences for sellers, it had limitations.
+For instance, it might not have fully considered other factors influencing decisions, such as individual experience, market conditions, and specific information provided by sellers.
+Additionally, the artificial setting of the experimental environment might limit the generalizability of the results.
+The analysis of the third experiment, although revealing potential gender impacts on economic decisions, might not have fully considered other influencing factors, such as individuals' financial knowledge, past experiences, and socio-economic backgrounds.
+Furthermore, the experimental setup might have been too simplistic, failing to capture all complexities of real-world decision-making.
+Despite the valuable insights provided by the fourth experiment regarding the relationship between gender and risk preferences, it too had limitations.
+First, the experimental setting might not have adequately simulated the complex decision-making environment of the real world, especially in financial market investment decisions.
+Second, the experiment might not have considered individuals' financial knowledge, experience, and other socio-economic factors that could affect risk preferences.
+Overall, while these experiments provided valuable insights into the role of gender in economic decision-making, they also had limitations, including the possibility that the simplified experimental settings might not fully simulate the complexity of the real world and the lack of consideration for individual experiences, socio-economic backgrounds, and other factors.
+
+### Future Directions and How to Continue:
+For Experiment 1, to further understand the role of gender in economic decision-making, future research needs to adopt a more comprehensive approach that considers a broader range of socio-economic factors and individual differences.
+Additionally, studies can explore how gender affects individuals' perceptions of and strategies for dealing with economic risks, and how these differences impact individuals' long-term economic well-being.
+Cross-cultural studies could further investigate how gender impacts economic decision-making across different socio-cultural backgrounds.
+Moreover, qualitative research methods such as in-depth interviews and case studies will help reveal the psychological dynamics and social influences behind decisions, providing richer insights for developing more effective economic policies and educational programs.
+For Experiment 2, future research should explore more factors influencing the choice of sellers, such as the dynamics between sellers and buyers, the impact of marketing strategies, and how personal characteristics of sellers affect buyers' choices.
+By using a more diverse sample of participants, increasing the complexity of scenarios, and applying mixed-methods research designs, our understanding of how gender influences economic decisions can be enhanced.
+Furthermore, considering how cultural and socio-economic factors shape gender roles is also an important direction for future research.
+For Experiment 3, future research needs to explore other variables beyond gender that affect economic decisions and attempt to replicate these findings under more realistic conditions.
+Additionally, studies should consider how cultural differences and social structures shape economic behavior and how education and policy interventions can mitigate the adverse effects of gender differences.
+Through more in-depth quantitative and qualitative research, a more comprehensive understanding of how individuals make decisions in different economic contexts can be achieved.
+For Experiment 4, future research should investigate gender differences across more dimensions, including how education and policy interventions can balance these differences.
+Studies could be extended to individuals across different cultural and social backgrounds to explore how cultural factors influence the relationship between gender and economic decisions.
+Furthermore, using qualitative methods to delve into the motivations and emotional factors behind individual decisions is also an important direction for future research.
+By combining quantitative data and qualitative insights, a more comprehensive understanding of the role of gender in economic decision-making can be developed, providing a basis for designing more effective financial planning and educational strategies.
+Overall, future research needs to take a more holistic approach to explore how factors beyond gender affect economic decisions and how these decisions change over time and across contexts.
+Cross-cultural comparative studies can reveal how gender roles in different socio-cultural backgrounds shape economic behavior.
+At the same time, in-depth qualitative research will help understand the psychological motivations behind decisions, offering richer insights for designing targeted economic policies and educational plans.
+
 ## Apenndix
+
+### Data Sample
+
+```{r tbl-table1, echo=FALSE, tbl.caption="Sample of the Cleaned Data for Money Illusion Study - Question 1"}
+# Select the required columns
+selected_data <- data %>%
+  select(ID, gênero, economicam, felicidade, atratividade_trab)
+
+# Translate column names to English for the table display
+colnames(selected_data) <- c("ID", "Gender", "Economic Term", "Happiness", "Job Attractiveness")
+
+# Create a table with the selected data for the first 6 rows with an English caption
+knitr::kable(head(selected_data, 6), 
+             format = "markdown",
+             booktabs = TRUE)
+```
+As shown in Table @tbl-table1, the data illus
+
+```{r table2, echo=FALSE}
+# Select the required columns
+selected_data <- data %>%
+  select(1:2, 12:14)
+
+# Translate column names to English for the table display
+colnames(selected_data) <- c("ID", "Gender", "Andre", "Bento", "Marcelo")
+
+# Create a table with the selected data for the first 6 rows with an English caption
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Data for Money Illusion Study - Question 2",
+             format = "markdown")
+```
+
+```{r table3, echo=FALSE}
+# Select the desired columns for the table
+selected_data <- data %>%
+  select(1:2, 7:8)
+
+# Translate column names to English for the table display
+colnames(selected_data) <- c("ID", "Gender", "Selling Chair - Real", "Buying Chair - Real")
+
+# Create a table with the selected data for the first 6 rows with an English caption
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Data for Money Illusion Study - Question 3",
+             format = "markdown")
+```
+
+```{r table4, echo=FALSE}
+selected_data <- data %>%
+  select(1:5)
+
+# Translate column names to English for the table display
+colnames(selected_data) <- c("ID", "Gender", "Contract Type AB", "Contract Type CD", "Contract Type EF")
+
+# Create a table with the selected data for the first 6 rows with an English caption
+knitr::kable(head(selected_data, 6), 
+             caption = "Sample of the Cleaned Data for Money Illusion Study - Question 4",
+             format = "markdown")
+```
 

### 2024-02-15 scripts/00-simulate-data.R

@@ -1,0 +1,38 @@
+library(tidyverse)
+
+set.seed(123)
+
+n_participants <- 1000
+
+participants <- tibble(
+  ID = 1:n_participants,
+  gender = sample(c("Female", "Male"), n_participants, replace = TRUE)
+)
+
+economic_conditions <- tibble(
+  economicam = sample(c("Carolina", "Maria"), n_participants, replace = TRUE),
+  felicidade = sample(c("Low", "Medium", "High"), n_participants, replace = TRUE),
+  atratividade_trab = sample(c("Low", "High"), n_participants, replace = TRUE)
+)
+
+seller_choices <- tibble(
+  A_casa_1 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE),
+  A_casa_2 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE),
+  A_casa_3 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE)
+)
+
+buy_sell_decisions <- tibble(
+  poltrona_venda_reais = sample(c("Less", "More", "Same"), n_participants, replace = TRUE),
+  poltrona_compra_reai = sample(c("Less", "More", "Same"), n_participants, replace = TRUE),
+  poltrona_venda_porce = sample(c("Less", "More", "Same"), n_participants, replace = TRUE)
+)
+
+contract_choices <- tibble(
+  contrato_AB = sample(c("A", "B"), n_participants, replace = TRUE),
+  contrato_CD = sample(c("C", "D"), n_participants, replace = TRUE),
+  contrato_EF = sample(c("E", "F"), n_participants, replace = TRUE)
+)
+
+simulated_data <- bind_cols(participants, economic_conditions, seller_choices, buy_sell_decisions, contract_choices)
+
+head(simulated_data)

### 2024-02-15 outputs/paper/paper.qmd
added new sections

@@
 ### Measurement
+
+Some specific adjustments have been made in order to ensure the relevance of questionnaire to the Brazilian context.
+The data of this paper collected by an online survey with 18 years or older participants who are consenting to participate.
+The Research Ethics Committee of the Pontifical Catholic University of São Paulo (PUC-SP) in 2021 approved this study(Certificate of Presentation for EthicalEvaluation [CAAE]: 44181621.8.0000.5482, approval number 4.681.515).
+
+There are no extra financial compensation for the involvement of Participants.
+It is not mandatory for participants to complete all problems, even if they completing one problem will also contributed to the analysis.
+The self-administered questionnaire was created by Qualtrics XM platform which adapting the structure from a previous research by Ziano et al.
+(2021).
+Researchers hand out the questionnaire link through social networks.
+From December 2021 to July 2022, data were collected online through 8 months.
+
+Researchers documented both the plan of research and data analysis on the Open Science Framework (OSF) before data collection 
+(accessible at: https://osf.io/2gkxf) in order to inherting the principles of reproducible research.
+The plan outlined the concept ofesearch objectives, money illusion, power analysis, hypotheses, relevant literature, methodology for result analysis, translated and adapted problem statements and other pertinent details.
+All datasets, statistical analyses and materials are available on the OSF platform (https://osf.io/48pqu/).
 
@@
 
-```{r tbl-table1, echo=FALSE, tbl.caption="Sample of the Cleaned Data for Money Illusion Study - Question 1"}
+```{r}
+#| label: tbl-table1
+#| tbl-cap: Sample of the Cleaned Data for Money Illusion Study - Question 1
+#| echo: false
+#| 
 # Select the required columns

### 2024-02-15 scripts/00-simulate-data.R

@@ -1,38 +1,51 @@
+# install necessary libraries
+install.packages("tidyverse")
+
+# Load necessary libraries
 library(tidyverse)
 
+# Set a seed for reproducibility
 set.seed(123)
 
+# Define the number of participants
 n_participants <- 1000
 
+# Create a dataframe with participant IDs and genders
 participants <- tibble(
   ID = 1:n_participants,
   gender = sample(c("Female", "Male"), n_participants, replace = TRUE)
 )
 
+# Generate economic conditions with random assignments
 economic_conditions <- tibble(
   economicam = sample(c("Carolina", "Maria"), n_participants, replace = TRUE),
   felicidade = sample(c("Low", "Medium", "High"), n_participants, replace = TRUE),
   atratividade_trab = sample(c("Low", "High"), n_participants, replace = TRUE)
 )
 
+# Randomly assign seller choices among three options
 seller_choices <- tibble(
   A_casa_1 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE),
   A_casa_2 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE),
   A_casa_3 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE)
 )
 
+# Create buy/sell decisions with random choices of 'Less', 'More', 'Same'
 buy_sell_decisions <- tibble(
   poltrona_venda_reais = sample(c("Less", "More", "Same"), n_participants, replace = TRUE),
   poltrona_compra_reai = sample(c("Less", "More", "Same"), n_participants, replace = TRUE),
   poltrona_venda_porce = sample(c("Less", "More", "Same"), n_participants, replace = TRUE)
 )
 
+# Randomly assign contract choices for AB, CD, EF
 contract_choices <- tibble(
   contrato_AB = sample(c("A", "B"), n_participants, replace = TRUE),
   contrato_CD = sample(c("C", "D"), n_participants, replace = TRUE),
   contrato_EF = sample(c("E", "F"), n_participants, replace = TRUE)
 )
 
+# Combine all the generated data into a single dataframe
 simulated_data <- bind_cols(participants, economic_conditions, seller_choices, buy_sell_decisions, contract_choices)
 
+# Display the first few rows of the simulated dataset
 head(simulated_data)

### 2024-02-15 scripts/01-cleanup-data.R

@@ -14,15 +14,15 @@ library(here)
 input_file_path <- here("inputs", "data", "money_data_raw.xlsx")
 output_file_path <- here("outputs", "data", "cleaned_money_data.csv")
 
-# Read the raw data-set
+# Step 0: Read the raw data-set
 raw_data <- readxl::read_excel(input_file_path)
 
-# Remove the first row from the data-set
+# Step 1: Remove the first row from the data-set
 # This row is used to store the description about the column name
 cleaned_data <- raw_data %>% 
   slice(-1)
 
-# Remove unnecessary columns for this study
+# Step 2: Remove unnecessary columns for this study
 # We only want the gender column and response choices columns
 cleaned_data <- cleaned_data %>%
   select(
@@ -41,9 +41,9 @@ cleaned_data <- cleaned_data %>%
     -`setal1997-funnel`
   )
 
-# Remove rows where gender is NA
+# Step 3: Remove rows where gender is NA
 cleaned_data <- cleaned_data %>%
   filter(!is.na(gênero) & gênero != 'Outro')
 
-# Save the cleaned dataset to a CSV file
+# Step 4: Save the cleaned dataset to a CSV file
 write.csv(cleaned_data, output_file_path, row.names = FALSE)

### 2024-02-15 scripts/02-test-data-validity.R

@@ -19,22 +19,18 @@ data <- read_csv(file_path)
 # No NA in the 'gênero' column
 test_gênero_NA <- all(!is.na(data$gênero))
 
-
 # Test 2: Total entries are more than 300
 test_entries_over_300 <- nrow(data) > 300
-
 
 # Test 3: Gender only contains male or female 
 # 'gênero' column contains only 'Mulher' and 'Homem'
 test_gênero_values <- all(data$gênero %in% c('Mulher', 'Homem'))
-
 
 # Test 4: Testing question 1 response only contain expected values
 # "economicam", "felicidade", "atratividade_trab" columns only have values 'Carolina', 'Maria', or NA
 test_specific_values <- all(sapply(data[c("economicam", "felicidade", "atratividade_trab")], function(x) {
   all(x %in% c('Carolina', 'Maria', NA))
 }))
-
 
 # Test 5:Testing question 2 response only contain expected values 
 # Columns have values 'Igual', 'Menos suscetível', or NA
@@ -43,13 +39,11 @@ test_casa_values <- all(sapply(data[c("A casa_1", "A casa_2", "A casa_3")], func
 }))
 print(paste("Test 5 - Casa columns contain only 1, 2, 3, or NA:", test_casa_values))
 
-
 # Test 6: Testing question 3 response only contain expected values 
 # Columns "A casa_1", "A casa_2", "A casa_3" contain only values 1, 2, 3, or NA
 test_poltrona_values <- all(sapply(data[c("poltrona_venda_reais", "poltrona_compra_reai", "poltrona_venda_porce")], function(x) {
   all(x %in% c('Igual', 'Menos suscetível', 'Mais suscetível', NA))
 }))
-
 
 # Test 7: 
 # "contrato_AB" contains only "A", "B", or NA; "contrato_CD" contains only "C", "D", or NA; "contrato_EF" contains only "E", "F", or NA

### 2024-02-15 outputs/paper/paper.qmd
added new tables

@@
 link-citations: true
+editor: 
+  markdown: 
+    wrap: sentence
 ---
@@
 
-Money illusion refers to a cognitive bias where individuals tend to assess the value of money solely based on its nominal value.
+Money illusion refers to a cognitive bias where individuals tend to assess the valueof money solely based on its nominal value.
 The real value of money is the nominal value of money plus the inlation rate.
-thereby overlooking the impact of inflation.
-This bias can lead to various consequences, such as reluctance to sell assets due to perceived nominal losses, misunderstanding wage increases, and more.
+thereby overlooking the impact of inflation.This bias can lead to various consequences, such as reluctance to sell assets due to perceived nominal losses, misunderstanding wage increases, and more.
 
@@
 Robert J.
-Shiller, a professor of economics at Yale University in the United States, believes that it is the false logic caused by the monetary illusion that led to the real estate bubble, "people mostly only remember the price of a few years ago when they bought a house, but often forget the price of other goods, andmistakenly believe that house prices have risen more than other prices." Thus exaggerating the investment potential of real estate"[@Shiller].
+Shiller, a professor of economics at Yale University in the United States, believes that it is the false logic caused by the monetary illusion that led to the real estate bubble, "people mostly only remember the price of a few years ago when they bought a house, but often forget the price of other goods, andmistakenly believe that house prices have risen more than other prices." Thus exaggerating the investment potential of real estate"[@shiller2014].
 
-From a stereotypical perspective, women is more emotional than men in the aspect of luxury consumptions, despite similar functional value to non-luxury brands, luxury brands command higher prices, especially among female consumers[@stokburger2013luxury].
-
-For decades, economists have debated whether the money illusion is real or, more generally, whether there are irrational influences in economic transactions.
-Milton Friedman, the famous monetary theorist, assumed that employers and consumers were rational, paying wages or buying goods with inflation in mind.
+For decades, economists have debated whether the money illusion is real or, more generally, whether there are irrational influences in economic transactions.Milton Friedman, the famous monetary theorist, assumed that employers and consumers were rational, paying wages or buying goods with inflation in mind.
 In other words, they can accurately judge the true value of a commodity[@friedman2010milton].
@@
 
-The original paper has 4 research problems: in problem 1, individuals inclined to perceive wage increases significantly in real term even if it is small in nominal terms; In problem 2, individuals will evaluate house deals based on nominal gains rather than real gains; In problem 3, participants will be less likely to purchase new items rather than second hand items when prices increase nominally; In problem 4, individuals might prefer riskier contracts in real terms over safer options presented in nominal terms.
-In this paper, we will focus on the relationship between gender and money illusion in the four research problems mentioned above.
+In this paper, we focus on the relationship between sex and money illusion in the four problems.
+According to the references we have found, women is more emotional than men in the aspect of luxury consumptions, despite similar functional value to non-luxury brands, luxury brands command higher prices, especially among female consumers[@stokburger2013luxury].
+
+Our hypothesis are across all four problems: Problem 1, gender and preference in economic decision making; Problem 2, Gender and seller choice; Problem 3, gender and market participation decisions; Problem 4, Gender and financial risk decision making.
+First of all, we choose the dataset from one replication of “Money Illusion”, then we cleaned the dataset and removed all unnecessary variables in dataset.
+We plot the graphs of among four problems for male and female respectively.
+Then we make analysis of it and verify whether we have evidence to against the hypothesis.
+Then we draw the conclusion and list the limitations of our study.
+
+The findings from experiments investigating gender differences in economic decision-making, highlighting distinct behaviors between men and women acrossvarious contexts, such as job attractiveness, seller selection, buying and selling strategies, and preferences for risky or risk-free contracts.
+It reveals that both genders show common concerns for economic stability, yet differ in their evaluation of career opportunities, decision-making strategies, and risk preferences.
+The discussion emphasizes the nuanced role of gender in economic decisions, suggesting further research to explore socio-economic factors, cross-cultural impacts, and psychological dynamics behind these decisions.
+The study acknowledges limitations due to its experimental design and calls for future research employing more comprehensive and realistic approaches to better understand gender influences in economic behavior.
 
@@
 The data of this paper collected by an online survey with 18 years or older participants who are consenting to participate.
-The Research Ethics Committee of the Pontifical Catholic University of São Paulo (PUC-SP) in 2021 approved this study(Certificate of Presentation for EthicalEvaluation [CAAE]: 44181621.8.0000.5482, approval number 4.681.515).
+The Research Ethics Committee of the Pontifical Catholic University of São Paulo (PUC-SP) in 2021 approved this study(Certificate of Presentation for EthicalEvaluation \[CAAE\]: 44181621.8.0000.5482, approval number 4.681.515).
 
@@
 It is not mandatory for participants to complete all problems, even if they completing one problem will also contributed to the analysis.
-The self-administered questionnaire was created by Qualtrics XM platform which adapting the structure from a previous research by Ziano et al.
-(2021).
+The self-administered questionnaire was created by Qualtrics XM platform which adapting the structure from a previous research by Ziano et al. (2021).
 Researchers hand out the questionnaire link through social networks.
@@
 
-Researchers documented both the plan of research and data analysis on the Open Science Framework (OSF) before data collection 
-(accessible at: https://osf.io/2gkxf) in order to inherting the principles of reproducible research.
+Researchers documented both the plan of research and data analysis on the Open Science Framework (OSF) before data collection (accessible at: https://osf.io/2gkxf) in order to inherting the principles of reproducible research.
 The plan outlined the concept ofesearch objectives, money illusion, power analysis, hypotheses, relevant literature, methodology for result analysis, translated and adapted problem statements and other pertinent details.
@@
 
-**Hypothetical Analysis:**
-Gender Perspectives on Economic Decisions: The graph suggests that men favored "Carolina" in economic terms and "Maria" in job attractiveness.
+**Hypothetical Analysis:** Gender Perspectives on Economic Decisions: The graph suggests that men favored "Carolina" in economic terms and "Maria" in job attractiveness.
 This could hypothetically indicate that men associate the concept of "Carolina" with economic stability and "Maria" with professional opportunities.
@@
 ```
+
 Observations from @fig-problem1-female for female participants' choices:
@@
 ```
+
 Observations from @fig-problem1-male for male participants' choices:
@@
 \newpage
+
 ### Problem 2: Gender and Seller Choice
@@
 ```
-Observations from @fig-problem2-female for female participants' choices:
-First Choice:
+
+Observations from @fig-problem2-female for female participants' choices: First Choice:
 
@@
 ```
+
 Observations from @fig-problem2-male Male Participants' Choices:
 
-First Choice:
-Andre has the highest preference as the first choice among male participants.
+First Choice: Andre has the highest preference as the first choice among male participants.
 Bento is the least preferred as the first choice.
@@
 
-Second Choice:
-Andre's preference decreases significantly from the first to the second choice.
+Second Choice: Andre's preference decreases significantly from the first to the second choice.
 Bento is the most preferred as the second choice, showing a substantial increase from the first choice.
@@
 
-Third Choice:
-Andre has a moderate increase in preference as the third choice.
+Third Choice: Andre has a moderate increase in preference as the third choice.
 Bento's preference drops slightly from the second choice.
@@
 \newpage
+
 ### Problem 3: Gender and Market Participation Decisions
@@
 ```
+
 Observations from @fig-problem3-female for female participants' choices:
@@
 ```
+
 Observations from @fig-problem3-male for male participants' choices:
@@
 \newpage
+
 ### Problem 4: Gender and Financial Risk Decision-Making
 
-**Hypothetical Analysis:**
-Gender Perspectives on Financial Risk Decisions: The graphs for Money Illusion Experiment 4 reveal the choices of male and female participants regarding different contract types characterized as riskless and risky across real, nominal, and neutral terms.
+**Hypothetical Analysis:** Gender Perspectives on Financial Risk Decisions: The graphs for Money Illusion Experiment 4 reveal the choices of male and female participants regarding different contract types characterized as riskless and risky across real, nominal, and neutral terms.
 
@@
 ```
+
 Observations from @fig-problem4-female for female participants' choices:
@@
 ```
+
 Observations from @fig-problem4-male for male participants' choices:
@@
 ### Future Directions and How to Continue:
+
 For Experiment 1, to further understand the role of gender in economic decision-making, future research needs to adopt a more comprehensive approach that considers a broader range of socio-economic factors and individual differences.
@@
 ```
-As shown in Table @tbl-table1, the data illus
 
-```{r table2, echo=FALSE}
+In this @tbl-table1 which reflects responses to a study on money illusion in Brazil, participants were asked to consider scenarios involving two workers, Maria and Carolina.
+Maria is the worker who received a real salary increase, which is an important detail for interpreting the Economic Term and Job Attractiveness columns.
+Respondents chose between "Maria" or "Carolina" for the person more likely to leave her job.
+The column "Happiness" is not filled in this excerpt, and "NA" indicates no choice was made by some respondents for certain questions.
+The Gender column distinguishes between "Mulher" (female) and "Homem" (male).
+
+```{r}
+#| label: tbl-table2
+#| tbl-cap: Sample of the Cleaned Data for Money Illusion Study - Question 2
+#| echo: false
+#| 
 # Select the required columns
@@
 knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Data for Money Illusion Study - Question 2",
              format = "markdown")
@@
 
-```{r table3, echo=FALSE}
+This @tbl-table2 represents a subset of data from a study examining money illusion, specifically focusing on Question 2 where participants ranked three house sellers—André, Bento, and Marcelo—according to the perceived success of their transactions.
+A response with ranking of "1" signifies the best deal, suggesting the most favorable outcome for the seller, whereas a "3" indicates the least favorable or worst deal.
+The table lists the participant's gender as "Mulher" for female and "Homem" for male, followed by their rankings for each seller.
+The actual ranking is: Marcelo as the top seller (1), Bento in the middle (2), and André as the least successful (3).
+
+```{r}
+#| label: tbl-table3
+#| tbl-cap: Sample of the Cleaned Data for Money Illusion Study - Question 3
+#| echo: false
+#| 
 # Select the desired columns for the table
@@
 knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Data for Money Illusion Study - Question 3",
              format = "markdown")
 ```
+The @tbl-table3 represents data from a study examining the concept of money illusion in decision-making, specifically regarding the perceived value of buying and selling under inflationary conditions.
+The participants, identified by gender and denoted as 'Mulher' for female and 'Homem' for male, were asked to evaluate their propensity to buy or sell a chair given changes in real value.
+The terms "Menos suscetível" (Less susceptible), "Igual" (Same), and "Mais suscetível" (More susceptible) indicate the participants' likelihood of buying or selling the chair, with 'NA' representing a lack of response.
+This part of the study probes whether inflationary illusions affect individuals' willingness to engage in transactions, contrasting their readiness to sell against their inclination to buy.
 
-```{r table4, echo=FALSE}
+```{r}
+#| label: tbl-table4
+#| tbl-cap: Sample of the Cleaned Data for Money Illusion Study - Question 4
+#| echo: false
+#| 
 selected_data <- data %>%
@@
 knitr::kable(head(selected_data, 6), 
-             caption = "Sample of the Cleaned Data for Money Illusion Study - Question 4",
              format = "markdown")
 ```
+
+The @tbl-table4 displays a subset of responses from a study exploring the influence of money illusion on contract selection.
+Participants, differentiated by gender as 'Mulher' for female and 'Homem' for male, had to choose between contracts labeled A, B, C, D, E, and F under varying conditions reflecting different levels of risk.
+Contract types AB, CD, and EF correspond to different framing conditions: nominal, real, or neutral.
+Contracts A, C, and E represent riskier options with certain nominal returns but uncertain real returns, capturing the essence of money illusion if chosen.
+The responses marked 'NA' indicate where participants did not make a selection.
+This component of the study aimed to determine whether participants' contract choices were swayed by nominal versus real terms, signifying the presence of money illusion.
 
@@
 The simulated dataset, designed to mirror the structure of the actual "Money Illusion" dataset, can be found at `scripts/00-simulate-data_data.R`.
-This script meticulously generates a dataset of 100 hypothetical delay instances.
-
-### Download Data from Open Science Framework
-
-Interested researchers can access the original dataset from the Brazilian researchers for further analysis or replication studies at the following URL: https://osf.io/48pqu/
+This script meticulously generates a dataset of 1000 hypothetical survey response instances.
 

### 2024-02-15 outputs/paper/paper.qmd
fixed issues

@@
 Robert J.
-Shiller, a professor of economics at Yale University in the United States, believes that it is the false logic caused by the monetary illusion that led to the real estate bubble, "people mostly only remember the price of a few years ago when they bought a house, but often forget the price of other goods, andmistakenly believe that house prices have risen more than other prices." Thus exaggerating the investment potential of real estate"[@shiller2014].
+Shiller, a professor of economics at Yale University in the United States, believes that it is the false logic caused by the monetary illusion that led to the real estate bubble, "people mostly only remember the price of a few years ago when they bought a house, but often forget the price of other goods, andmistakenly believe that house prices have risen more than other prices." Thus exaggerating the investment potential of real estate"[@Shiller_2014].
 
@@
 
-The data were collected via an online survey platform and include a range of variables:
+The data were collected via an online survey platform of and include a range of variables:
 
@@
 These serve as a quality control measure, filtering for data quality and comprehension.
+
+### Variable Description
+
+This study serves as a reproduction and further exploration of the seminal work on the money illusion effect, particularly examining the impact of gender on financial decision-making.
+Utilizing identical datasets as the original paper, our analysis narrows the focus to the variable of gender.
+
+Question 1 Variables:
+
+- ID: Unique identifier for each participant.
+- Gender (gênero): The gender of the participant, recorded as 'Mulher' for female and 'Homem' for male.
+- Economic Term (economicam): Choice of the individual more likely to leave their job, between 'Carolina' and 'Maria'.
+- Happiness (felicidade): The happiness level, which is not filled in the provided data excerpt.
+- Job Attractiveness (atratividade_trab): The perceived job attractiveness with choices being 'Carolina' or 'Maria'.
+
+Question 2 Variables:
+
+- ID: Unique identifier for each participant.
+- Gender (gênero): The gender of the participant, recorded as 'Mulher' for female and 'Homem' for male.
+- Andre (A Casa_1): the actual least seller, recorded as 1, 2, 3 for participant's ranking with 1 represent the best.
+- Bento (A casa_2): the actual middle seller, recorded as 1, 2, 3 for participant's ranking with 1 represent the best.
+- Marcelo (A casa_3): the actual top seller, recorded as 1, 2, 3 for participant's ranking with 1 represent the best.
+
+Question 3 Variables:
+
+- ID: Unique identifier for each participant.
+- Gender (gênero): The gender of the participant, recorded as 'Mulher' for female and 'Homem' for male.
+- Selling Chair - Real (poltrona_venda_reais): The likelihood of selling a chair when considering real value changes.
+- Buying Chair - Real (poltrona_compra_reai): The likelihood of buying a chair when considering real value changes.
+
+Question 4 Variables:
+
+- ID: Unique identifier for each participant.
+- Gender (gênero): The gender of the participant, recorded as 'Mulher' for female and 'Homem' for male.
+- Contract Type AB (contrato_AB): The type of contract chosen by the participant, with 'A' indicating a risky contract and 'B' indicating a less risky contract.
+- Contract Type CD (contrato_CD): Similar to AB, with 'C' indicating a risky contract and 'D' indicating a less risky contract.
+- Contract Type EF (contrato_EF): Similar to the above, with 'E' indicating a risky contract and 'F' indicating a less risky contract.
 
@@
 ```
+
 The @tbl-table3 represents data from a study examining the concept of money illusion in decision-making, specifically regarding the perceived value of buying and selling under inflationary conditions.
@@
 
-Data cleaning is a critical step in ensuring the accuracy and reliability of the analysis.
-The detailed procedure and the R script used for data cleaning are available in `scripts/01_cleanup_data.R`.
-The script elucidates the steps taken to refine the dataset by filtering out incomplete records and unnecessary columns for this study.
-The steps are: 1.
-Remove the first row in the dataset, since it is used to store the description to the column name.
-2.
-Remove unnecessary columns for this study, by only keep the gender and responses columns.
-3.
+Data cleaning is a critical step in ensuring the accuracy and reliability of the analysis.The detailed procedure and the R script used for data cleaning are available in `scripts/01_cleanup_data.R`.The script elucidates the steps taken to refine the dataset by filtering out incomplete records and unnecessary columns for this study.
+The steps are: 1.Remove the first row in the dataset, since it is used to store the description to the column name.2.
+Remove unnecessary columns for this study, by only keep the gender and responses columns.3.
 Remove all gender rows with 'na' since this study is focusing on the behavior for money illusion for male and female participants.

### 2024-02-15 outputs/paper/paper.qmd
fixed issue

@@
 
-### Measurement
+### Measurement and Data Collection
 
-Some specific adjustments have been made in order to ensure the relevance of questionnaire to the Brazilian context.
-The data of this paper collected by an online survey with 18 years or older participants who are consenting to participate.
-The Research Ethics Committee of the Pontifical Catholic University of São Paulo (PUC-SP) in 2021 approved this study(Certificate of Presentation for EthicalEvaluation \[CAAE\]: 44181621.8.0000.5482, approval number 4.681.515).
+To contextualize the study within the Brazilian socio-economic environment, Brazilian researchers tailored the survey instrument while maintaining the core essence of the original study.
+A cross-sectional online survey was conducted with the prerequisites that participants be at least 18 years old and give their consent.
+The study received ethical clearance from the Pontifical Catholic University of São Paulo's Research Ethics Committee in 2021.
 
-There are no extra financial compensation for the involvement of Participants.
-It is not mandatory for participants to complete all problems, even if they completing one problem will also contributed to the analysis.
-The self-administered questionnaire was created by Qualtrics XM platform which adapting the structure from a previous research by Ziano et al. (2021).
-Researchers hand out the questionnaire link through social networks.
-From December 2021 to July 2022, data were collected online through 8 months.
+Participation was voluntary and uncompensated, and participants had the option to respond to any number of the problems presented.
+Data were captured using the Qualtrics XM platform over eight months, from December 2021 to July 2022, and were distributed via social media.
 
-Researchers documented both the plan of research and data analysis on the Open Science Framework (OSF) before data collection (accessible at: https://osf.io/2gkxf) in order to inherting the principles of reproducible research.
-The plan outlined the concept ofesearch objectives, money illusion, power analysis, hypotheses, relevant literature, methodology for result analysis, translated and adapted problem statements and other pertinent details.
-All datasets, statistical analyses and materials are available on the OSF platform (https://osf.io/48pqu/).
+The survey gathered socio-demographic information and responses to four problems designed to assess susceptibility to money illusion in contexts such as salary increases, real estate transactions, purchasing/selling decisions, and risk susceptibility.
+The survey also included verification questions to ensure participant comprehension and to act as a quality control mechanism.
 

### 2024-02-15 scripts/00-simulate-data.R

@@ -1,51 +1,60 @@
-# install necessary libraries
+# Install the 'tidyverse' package if not already installed. 
+# 'tidyverse' is a collection of R packages designed for data science.
 install.packages("tidyverse")
 
-# Load necessary libraries
+# Load the 'tidyverse' package to use its functions.
 library(tidyverse)
 
-# Set a seed for reproducibility
+# Set a seed to ensure that the random number generation is reproducible.
+# This means you'll get the same random numbers each time you run the script.
 set.seed(123)
 
-# Define the number of participants
+# Define the number of participants for the simulation.
 n_participants <- 1000
 
-# Create a dataframe with participant IDs and genders
+# Create a tibble (a type of dataframe) with participant IDs and assigned genders.
+# 'sample' randomly selects from the given vectors, with replacement allowing repeats.
 participants <- tibble(
   ID = 1:n_participants,
   gender = sample(c("Female", "Male"), n_participants, replace = TRUE)
 )
 
-# Generate economic conditions with random assignments
+# Generate a tibble of economic conditions, randomly assigning values for economic perception,
+# happiness level, and job attractiveness.
 economic_conditions <- tibble(
   economicam = sample(c("Carolina", "Maria"), n_participants, replace = TRUE),
   felicidade = sample(c("Low", "Medium", "High"), n_participants, replace = TRUE),
   atratividade_trab = sample(c("Low", "High"), n_participants, replace = TRUE)
 )
 
-# Randomly assign seller choices among three options
+# Randomly generate seller choices among three options for each participant.
+# This simulates participants' choices for three different house sellers.
 seller_choices <- tibble(
   A_casa_1 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE),
   A_casa_2 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE),
   A_casa_3 = sample(c("Andre", "Bento", "Marcelo"), n_participants, replace = TRUE)
 )
 
-# Create buy/sell decisions with random choices of 'Less', 'More', 'Same'
+# Create tibble for buy/sell decisions with random choices between 'Less', 'More', and 'Same'.
+# This could simulate participants' decisions to buy or sell a chair given varying prices.
 buy_sell_decisions <- tibble(
   poltrona_venda_reais = sample(c("Less", "More", "Same"), n_participants, replace = TRUE),
[…]

### 2024-02-15 scripts/01-cleanup-data.R

@@ -1,49 +1,0 @@
-# install necessary libraries
-install.packages("dplyr")
-install.packages("readxl")
-install.packages("here")
-
-# Load necessary libraries
-library(readxl)
-library(dplyr)
-library(here)
-
-# Use the `here` function to specify file paths relative to the project root
-# These variables are used to store the file path to get the file before 
-# data cleaning and save the file after data cleaning
-input_file_path <- here("inputs", "data", "money_data_raw.xlsx")
-output_file_path <- here("outputs", "data", "cleaned_money_data.csv")
-
-# Step 0: Read the raw data-set
-raw_data <- readxl::read_excel(input_file_path)
-
-# Step 1: Remove the first row from the data-set
-# This row is used to store the description about the column name
-cleaned_data <- raw_data %>% 
-  slice(-1)
-
-# Step 2: Remove unnecessary columns for this study
-# We only want the gender column and response choices columns
-cleaned_data <- cleaned_data %>%
-  select(
-    -idade, 
-    -gênero_3_TEXT, 
-    -decl_racial, 
-    -decl_racial_5_TEXT, 
-    -escolaridade, 
-    -escolaridade_transf, 
-    -área_estudo, 
-    -curso, 
-    -cidade_bairro_1, 
-    -renda, 
-    -renda_e_pessoas,
-    -verif_maria,
-    -`setal1997-funnel`
-  )
-
-# Step 3: Remove rows where gender is NA
-cleaned_data <- cleaned_data %>%
-  filter(!is.na(gênero) & gênero != 'Outro')
-
-# Step 4: Save the cleaned dataset to a CSV file
-write.csv(cleaned_data, output_file_path, row.names = FALSE)

### 2024-02-15 scripts/01-download_data.R

@@ -1,0 +1,25 @@
+# install necessary libraries
+install.packages("httr")
+install.packages("here")
+
+# Load necessary libraries
+library(httr) # for HTTP requests, like GET
+library(here) # for constructing file paths that work across different operating systems
+
+# Specify the direct download link for the dataset file
+# Make sure this URL is the link to the file you intend to download
+file_url <- "https://osf.io/4x25f/download"
+
+# Specify the path where the downloaded file will be saved
+# 'here' constructs a path relative to the project's root directory,
+# ensuring that the script works seamlessly across different environments
+save_to <- here("inputs", "data", "money_data_raw.xlsx")
+
+# Perform the file download
+# The GET function sends an HTTP GET request to the specified URL
+# The write_disk function, with the path provided by 'here', writes the content of the response to disk
+# 'overwrite = TRUE' ensures that if the file already exists, it will be overwritten
+GET(file_url, write_disk(save_to, overwrite = TRUE))
+
+# After running this script, the file 'money_data_raw.xlsx' should be in the 'inputs/data' directory
+# of your project. Check this directory to verify the download.

### 2024-02-15 scripts/02-cleanup-data.R

@@ -1,0 +1,53 @@
+# Install necessary R packages if they are not already installed
+# dplyr for data manipulation, readxl for reading Excel files, and here for path management
+install.packages("dplyr")
+install.packages("readxl")
+install.packages("here")
+
+# Load the required libraries into the R session
+library(readxl) # For reading Excel files
+library(dplyr)  # For data manipulation functions
+library(here)   # For constructing portable paths
+
+# Set file paths using the `here` function, ensuring they work across different environments
+# `input_file_path` is the path where the raw Excel data file is located
+# `output_file_path` is where the cleaned data will be saved as a CSV file
+input_file_path <- here("inputs", "data", "money_data_raw.xlsx")
+output_file_path <- here("outputs", "data", "cleaned_money_data.csv")
+
+# Step 0: Read the raw data from the Excel file
+# The data is read into a dataframe `raw_data`
+raw_data <- readxl::read_excel(input_file_path)
+
+# Step 1: Clean the data by removing the first row, which contains column descriptions rather than data
+# The `slice` function from dplyr excludes the first row
+cleaned_data <- raw_data %>% 
+  slice(-1)
+
+# Step 2: Streamline the dataset by selecting only relevant columns for this analysis
+# Irrelevant columns such as demographic details and verification question responses are removed
+cleaned_data <- cleaned_data %>%
+  select(
+    -idade,                 # Age
+    -gênero_3_TEXT,         # Text response for gender
+    -decl_racial,           # Racial declaration
+    -decl_racial_5_TEXT,    # Text response for racial declaration
+    -escolaridade,          # Education level
+    -escolaridade_transf,   # Transferred education level
+    -área_estudo,           # Area of study
+    -curso,                 # Course
+    -cidade_bairro_1,       # Neighborhood and city
+    -renda,                 # Income
+    -renda_e_pessoas,       # Income per household
+    -verif_maria,           # Verification question for Maria
+    -`setal1997-funnel`     # Funnel questions from setal1997 study
+  )
+
+# Step 3: Filter out incomplete records, specifically those where the gender is missing or marked as 'Other'
+# This ensures the dataset only contains entries with specified gender information
+cleaned_data <- cleaned_data %>%
+  filter(!is.na(gênero) & gênero != 'Outro')
+
+# Step 4: Write the cleaned dataset to a CSV file, excluding row names for a tidier file
+# The resulting CSV file will be used for subsequent analysis
+write.csv(cleaned_data, output_file_path, row.names = FALSE)

### 2024-02-15 scripts/03-test-data-validity.R

@@ -45,7 +45,7 @@ test_poltrona_values <- all(sapply(data[c("poltrona_venda_reais", "poltrona_comp
   all(x %in% c('Igual', 'Menos suscetível', 'Mais suscetível', NA))
 }))
 
-# Test 7: 
+# Test 7: Testing question 4 response contains all valid responses
 # "contrato_AB" contains only "A", "B", or NA; "contrato_CD" contains only "C", "D", or NA; "contrato_EF" contains only "E", "F", or NA
 test_contrato_values <- all(data$contrato_AB %in% c("A", "B", NA)) &&
   all(data$contrato_CD %in% c("C", "D", NA)) &&

### 2024-02-15 outputs/paper/paper.qmd
fixed issue

@@
 Our findings highlight that the effects of money illusion may also vary by gender, showcasing distinct patterns of financial behavior between males and females."
-thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git; Replication on Social Science Reproduction platform available at: "
+thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
 author: "Terry Tu, Jingyi Shen, Yaning Jin "
@@
 
-**Hypothetical Analysis:** Gender Perspectives on Economic Decisions: The graph suggests that men favored "Carolina" in economic terms and "Maria" in job attractiveness.
-This could hypothetically indicate that men associate the concept of "Carolina" with economic stability and "Maria" with professional opportunities.
-Analyzing this alongside gender could reveal whether women make similar associations or have a contrasting view.
+The first analysis, we explored gender perspectives on economic decisions, focusing on preferences for "Carolina" and "Maria" in terms of economic advantage and job attractiveness.
+The indication of money illusion would be suggested if, for instance, male participants showed a preference for "Carolina" for economic stability and "Maria" for professional opportunities, while female participants exhibited similar or contrasting preferences, thereby revealing gender-specific biases in economic decision-making.
 
@@
 
-Economic Terms: A significant majority of female participants chose "Carolina" over "Maria" in economic terms.
-This choice distribution is similar to that of the male participants, suggesting a consensus across genders regarding economic choices tied to "Carolina".
-
-Happiness: Female participants seem evenly split between "Carolina" and "Maria" when it comes to happiness, which differs from male participants, who showed a slight preference for "Maria" in this condition.
+For the economic terms, a significant majority of female participants chose "Maria" over "Carolina" in economic terms.
+This choice distribution is similar to that of the male participants, suggesting a consensus across genders regarding economic choices tied to "Maria".
+For the happiness, female participants seem evenly split between "Carolina" and "Maria" when it comes to happiness, which differs from male participants, who showed a slight preference for "Carolina" in this condition.
 This could suggest that women see both "Carolina" and "Maria" as equally viable options for emotional fulfillment or that happiness is not as strongly associated with either choice as it is with economic terms.
-
-Job Attractiveness: The choices for job attractiveness among female participants are also evenly distributed between "Carolina" and "Maria", whereas male participants had a preference for "Maria".
-This could imply that for women, the qualities or opportunities represented by "Carolina" and "Maria" are equally attractive in a professional setting.
+For the job Attractiveness, the choices for job attractiveness among female participants had a preference for "Maria".
 
@@
 
-Economic Terms: A significant majority of male participants chose "Carolina" over "Maria" in economic terms.
-This indicates a strong preference for the economic implications associated with "Carolina" among male participants, suggesting they may perceive "Carolina" as a more stable or profitable economic choice.
-
-Happiness: The male participants' choices for happiness are nearly evenly split, with a slight preference for "Carolina." This distribution shows that men do not strongly associate either "Carolina" or "Maria" with happiness or that they see both options as similarly capable of providing emotional satisfaction.
-
-Job Attractiveness: Male participants displayed a clear preference for "Maria" in terms of job attractiveness.
+For the economic terms, a significant majority of male participants chose "Maria" over "Carolina" in economic terms.
+This indicates a strong preference for the economic implications associated with "Maria" among male participants, suggesting they may perceive "Maria" as a more stable or profitable economic choice.
+For the happiness, the male participants' choices for happiness are nearly evenly split, with a slight preference for "Maria." This distribution shows that men do not strongly associate either "Maria" or "Carolina" with happiness or that they see both options as similarly capable of providing emotional satisfaction.
+For the job Attractiveness, male participants displayed a clear preference for "Maria" in terms of job attractiveness.
 This could suggest that the attributes or opportunities associated with "Maria" resonate more with men when considering the attractiveness of a job or career path.
@@
 
-Economic Rationality: Both genders show a strong preference for "Carolina" in economic terms, which might suggest that "Carolina" represents a more financially beneficial or stable option.
-This similarity indicates that both men and women may prioritize financial stability in their decision-making processes.
-
-Emotional Considerations: The contrast in happiness choices between genders is subtle but present.
-Men's slight preference for "Maria" might suggest that they associate "Maria" with emotional well-being slightly more than women do.
-However, women's even split could indicate a balanced view or a lesser degree of differentiation between "Carolina" and "Maria" in terms of happiness.
-
-Professional Preferences: The difference in job attractiveness choices is more pronounced, with men preferring "Maria" and women showing no clear preference.
-This may suggest that men and women have different criteria for what makes a job attractive or that they value different aspects of a job.
+In the problem 1 we examining gender perspectives on economic decisions, specifically preferences between "Carolina" and "Maria" across economic advantage, happiness, and job attractiveness, we found intriguing differences and similarities between genders.
+Analysis revealed a consensus among both male and female participants, with a strong preference for "Maria" in economic terms, indicating a shared prioritization of financial stability.
+Interestingly, while men showed a slight preference for "Carolina" in the context of happiness, suggesting a nuanced difference in emotional satisfaction, women were evenly split between "Carolina" and "Maria," implying a more balanced view towards emotional fulfillment.
+Job attractiveness presented are the same; males and females both favored "Maria," suggesting a more good valuation of the professional attributes offered by "Maria." This gender comparison underscores the complexity of economic decision-making influenced by gender, with both shared views on economic rationality and distinct approaches to emotional and professional considerations.
+The results point towards a societal consensus on certain financial principles and happiness while also highlighting nuanced differences in how job attractiveness are perceived, potentially shaped by societal roles, individual experiences, or inherent biases.
+Such findings stress the importance of understanding gender perspectives in economic decisions, suggesting that while there may be common ground in economic choices and emotional satisfaction, there are significant differences in the valuation of job attractiveness.
+This analysis, however, is based on the specific context of our study and requires further exploration to understand the broader implications of these gender differences in economic decision-making.
 
@@
 
-**Hypothetical Analysis:**
-
-Gender Perspectives on Seller Choices: The graphs for Money Illusion Experiment 2 show distinct patterns in how male and female participants rank sellers—Andre, Bento, and Marcelo.
-Hypothetically, this could indicate that male participants associate Andre with immediate value or appeal, as evidenced by his high ranking as the first choice, while Bento and Marcelo may represent longer-term benefits or stability, which becomes more apparent in the subsequent choices.
-On the other hand, female participants show a strong initial preference for Marcelo, suggesting they may perceive Marcelo as a symbol of immediate trustworthiness or value.
-Bento's consistent middle-ground ranking among females could indicate a perception of balanced or average appeal.
-
-The preference dynamics could be interpreted as men being more likely to revise their initial judgments, while women might be consistent in their preferences.
-Analyzing these choices alongside gender could reveal whether men and women apply different criteria when evaluating the options presented to them, possibly due to differing risk assessments, values, or expectations in economic decisions.
-The shift in preferences for both genders as they move from first to third choice could suggest a complex decision-making process where initial impressions are adjusted upon further reflection or comparison.
+The second analysis, we examined gender perspectives on seller choices, evaluating preferences among "Andre," "Bento," and "Marcelo" based on their appeal and perceived value.
+The manifestation of the bias would be clear if male and female participants diverged in their rankings, perhaps preferring Marcelo for immediate trustworthiness or value, Andre for immediate appeal, and Bento for balanced appeal, indicating nuanced gender differences in evaluating seller attributes.
 
@@
 
-Andre appears to be the least favored as the first choice among female participants.
-Bento has a moderate preference as the first choice.
+For the first Choice, Bento appears to be the least favored as the first choice among female participants.
+Andre has a moderate preference as the first choice.
 Marcelo is the most preferred seller for the first choice.
-Second Choice:
-
-Andre sees a significant increase in preference from the first to the second choice.
+For the second Choice, Andre sees a decrease in preference from the first to the second choice.
 Bento is the most selected as the second choice.
 Marcelo's preference drops, making him the least favored for the second choice.
-Third Choice:
-
-Andre is again the least preferred as the third choice.
-Bento's preference decreases compared to the second choice.
-Marcelo's preference increases, making him the most favored for the third choice.
+For the third Choice, Bento is again the least preferred as the third choice.
+Andre's and  Marcelo's preference increases compared to the second choice.
+Andre became the most favored for the third choice.
 
@@
 
-First Choice: Andre has the highest preference as the first choice among male participants.
+For the first Choice, Andre has the highest preference as the first choice among male participants.
 Bento is the least preferred as the first choice.
 Marcelo has a moderate preference as the first choice.
-
-Second Choice: Andre's preference decreases significantly from the first to the second choice.
+For the second Choice, Andre's preference decreases significantly from the first to the second choice.
 Bento is the most preferred as the second choice, showing a substantial increase from the first choice.
 Marcelo's preference remains relatively stable across the first and second choices.
-
-Third Choice: Andre has a moderate increase in preference as the third choice.
-Bento's preference drops slightly from the second choice.
+For the third Choice, Andre has a moderate increase in preference as the third choice.
+Bento's preference drops from the second choice.
 Marcelo sees a significant increase and is the most favored as the third choice.
@@
 
-First Choice Dynamics:
-
-Male participants show a clear preference for Andre as their first choice, while female participants favor Marcelo.
-This difference could reflect varying criteria or perceptions of value between genders.
-Bento is the least favored first choice by males but holds a moderate preference among females, suggesting different initial impressions based on gender.
-Evolution of Preferences:
-
-Both genders show a shifting pattern in their preferences from the first to the third choice, indicating a reevaluation of the sellers as they move down the rank order.
-
-Andre's stark contrast between the first and subsequent choices in male participants could suggest a reconsideration of initial impressions after comparing all options.
-Consensus on Final Choices:
-
-Marcelo emerges as the most favored third choice for both genders, suggesting a commonality in the eventual perception of value or appeal.
+In our problem 2, investigation into gender dynamics within economic decision-making, particularly examining preferences for "Andre," "Bento," and "Marcelo" across first, second, and third choices, a detailed pattern of gender-based differences and evolving preferences emerged.
+The analysis disclosed a shared yet shifting perspective among male and female participants in their selection sequence.
+Initially, male participants predominantly favored "Andre" as their first choice, suggesting a distinct preference aligned with specific attributes or perceived benefits associated with "Andre." Conversely, female participants demonstrated a significant preference for "Marcelo," indicating differing priorities or perceived advantages.
+As participants progressed to their second and third choices, notable shifts in preferences were observed, reflecting a complex evaluative process.
+"Bento" emerged as a common preference across genders for the second choice, highlighting a reassessment of value or appeal.
+By the third choice, "Marcelo" gaining favor among males, and "Andre" gains favor among females.
+This analysis illuminates the nuanced nature of gender influences on economic decisions, revealing both shared and distinct patterns of preference evolution.
+The initial gender-specific choices evolve through a dynamic process of reevaluation, leading to a shared recognition of value in the final choice.
+This highlights the complexity of decision-making processes, influenced by a blend of societal roles, individual experiences, and perhaps inherent biases.
+These findings underscore the importance of acknowledging gender perspectives in understanding economic decision preferences, suggesting that while there may be commonalities in final choices, the journey to these decisions can significantly differ between genders.
+This exploration, rooted in the specific context of our study, calls for further investigation into the broader implications of gender differences in economic decision-making processes.
 
@@
 
-**Hypothetical Analysis:**
-
-Gender Perspectives on Financial Decisions: The graphs for Money Illusion Experiment 3 display the decision-making tendencies of male and female participants when faced with the option to buy or sell under varying conditions of likelihood ('More', 'Same', 'Less').
-Analyzing this alongside gender can reveal nuanced approaches to market engagement.
-This hypothetical analysis could be pointing to underlying gender differences in economic decision-making, where men might prioritize growth or investment maintenance, and women might prioritize financial security and opportunistic gains.
-However, it's crucial to approach these assumptions critically, as individual decisions are influenced by a range of personal, social, and economic factors beyond gender.
+The third analysis delved into gender perspectives on financial decisions, with participants choosing to buy or sell under conditions of varying likelihoods ('More', 'Same', 'Less').
+The presence of money illusion would be inferred if there were a gender-based pattern in the willingness to engage in financial transactions, reflecting underlying gender differences in risk tolerance and investment strategy.
 
@@
 
-Buy Decisions: Females show the least likelihood to buy more and a similar inclination to buy less or the same.
-This could indicate a cautious or conservative approach to purchasing decisions, possibly prioritizing stability or risk aversion.
-
-Sell Decisions: The tendency to sell more is considerably higher than to sell less, with selling the same as an intermediate option.
-This pattern might suggest a greater openness to divesting or capitalizing on assets when conditions are favorable, or it could reflect a strategic approach to managing investments.
+For the buy decisions, females show the least likelihood to buy more and a similar inclination to buy less or the same.
+For the sell decisions, the tendency to sell more is considerably higher than to sell less, with selling the "same" is the first choose.
 
@@
 
-Buy Decisions: Males show a balanced approach between buying more and the same, with less likelihood to buy less.
-This distribution could imply a more assertive or optimistic strategy toward acquiring assets or a greater confidence in market conditions.
-
-Sell Decisions: There is a strong preference for selling the same, followed by selling more, and the least for selling less.
-This could suggest a preference for maintaining the status quo or a calculated approach to selling, where changes in market conditions are considered but not reacted to hastily.
+For the buy decisions, males show a balanced approach between buying more and the same, with less likelihood to buy less.
+For the sell decisions, there is a strong preference for selling the same, followed by selling more, and the least for selling less.
 
@@
 
-Buying Behavior: Females appear more conservative, potentially weighing the risks more heavily, while males seem to demonstrate a readiness to invest, indicating a possible difference in risk tolerance.
-
-Selling Behavior: Females are more likely to sell more, which might suggest a strategy to capitalize on gains or avoid losses.
-In contrast, males' preference for selling the same amount could indicate a long-term investment strategy or a less reactive approach to market fluctuations.
+In our investigation into problem 3, focusing on gender dynamics within buying and selling decisions, we unveiled compelling gender-specific preferences that significantly enrich our understanding of economic behavior.
+The study meticulously examined the differences and similarities in how males and females approach financial transactions, particularly through the lens of risk tolerance and strategic financial planning.
+Our findings highlighted a shared emphasis on cautious financial management, yet revealed distinct gender-based strategies when delving deeper into the specifics of buying and selling actions.
+The analysis demonstrated a notable consensus in prioritizing financial prudence, with both genders exhibiting a strategic approach to economic transactions.
+However, the nuances in behavior became apparent when dissecting the data further.
+Females displayed a tendency towards conservatism in buying decisions, showing a lesser likelihood to increase their purchasing volume.
+This cautious approach suggests a higher degree of risk aversion, possibly rooted in a desire for financial stability or influenced by broader societal or individual factors.
+In contrast, males presented a more balanced buying strategy, showing an openness to both increasing and maintaining their purchase levels, which might indicate a more optimistic outlook on financial growth or a greater confidence in navigating market conditions.
+When analyzing selling behaviors, the Same choices for men and women.
+females and males both demonstrated a preference for maintaining their current asset levels, suggesting a long-term investment perspective or a cautious approach to market fluctuations.
+This gender comparison underscores the complexity of financial decision-making processes, revealing that while there is a shared foundation of financial caution, the methods and motivations driving these decisions diverge significantly between genders.
+The findings suggest that societal norms, personal experiences, and possibly inherent biases influence these economic behaviors, highlighting the importance of incorporating gender perspectives in financial decision-making studies.
+Such insights into buying and selling behaviors not only contribute to our understanding of economic dynamics but also suggest that gender differences in risk tolerance and financial strategy are crucial factors in economic decision-making.
 
@@
 
-**Hypothetical Analysis:** Gender Perspectives on Financial Risk Decisions: The graphs for Money Illusion Experiment 4 reveal the choices of male and female participants regarding different contract types characterized as riskless and risky across real, nominal, and neutral terms.
+The fourth analysis, we focused on gender perspectives on financial risk decisions, where participants were asked to choose between riskier and less risky contracts in nominal, real, or neutral terms.
+The evidence of the illusion would be apparent if participants, influenced by gender perspectives, showed distinct preferences for certain contracts, revealing a gendered approach to risk assessment in different economic scenarios.
 
@@
 
-Real Terms: Females show a preference for riskless contracts, potentially indicating a perception of real terms as more tangible and, thus, preferring security in transactions that are adjusted for inflation or reflect actual purchasing power.
-
-Nominal Terms: A slight preference for riskless contracts over risky ones in nominal terms could suggest a cautious approach towards transactions that are not adjusted for inflation, reflecting a concern for potential value loss over time.
-
-Neutral Terms: The distribution is more balanced, but still, riskless contracts are slightly preferred, which might indicate a general tendency towards caution regardless of the framing of terms.
+For the real terms, females show a preference for riskless contracts.
+For the nominal terms, a slight preference for riskless contracts over risky ones.
+For the neutral terms, the distribution is more balanced, but still, riskless contracts are slightly preferred.
 
@@
 
-Real Terms: Males show an overwhelming preference for riskless contracts in real terms, possibly valuing the certainty of returns that account for inflation and maintain purchasing power.
-
-Nominal Terms: The preference shifts towards risky contracts, implying that men might be more willing to engage in speculative transactions when dealing with nominal values that do not account for inflation.
-
-Neutral Terms: There is a nearly even split, with a slight lean towards riskless contracts, suggesting that without specific framing, men might default to a more balanced risk approach.
+For the real terms, males show an overwhelming preference for riskless contracts in real terms.
+For the nominal terms, the preference shifts towards riskless contracts.
+For the neutral terms, there is a nearly even split, with a slight lean towards risky contracts.
 
@@
 
-Risk Preferences in Real Terms: Both genders exhibit a strong preference for riskless contracts, possibly due to the direct impact of inflation-adjusted transactions on real-world purchasing power.
-
-Risk Preferences in Nominal Terms: A stark difference is observed; women remain cautious, whereas men become risk-takers, which could imply a gender-based divergence in responses to economic scenarios where inflation or value erosion is a factor.
-
-Risk Preferences in Neutral Terms: The slight preference for riskless contracts among both genders indicates a baseline aversion to risk when the terms are not clearly defined or when the framing is neutral.
+In our study examining gender perspectives on economic decisions, particularly in the context of contract preferences under different terms (real, nominal, and neutral), we observed distinct patterns between male and female participants.
+Females consistently demonstrated a preference for riskless contracts across all terms, with their preference being strongest in real terms and slightly less pronounced but still evident in nominal and neutral terms.
+This indicates a general female inclination towards financial stability and aversion to risk, regardless of the framing of the economic conditions.
+Males, on the other hand, showed a significant preference for riskless contracts in real terms, mirroring the strong aversion to risk seen in female preferences.
+However, when considering nominal terms, this preference, while still leaning towards riskless contracts, becomes less overwhelming, suggesting a somewhat greater tolerance for risk under conditions where the economic framing is less directly tied to tangible outcomes.
+Interestingly, in neutral terms, males displayed a nearly even split in their preferences, with a slight tendency towards risky contracts, indicating a nuanced shift towards risk acceptance when the economic decision-making context is perceived as more abstract or balanced.
+These findings highlight the complexity of economic decision-making influenced by gender, revealing both shared and divergent attitudes towards risk under varying economic framings.
+The gender comparison underscores a societal trend towards risk aversion, particularly in contexts closely associated with real-world financial stability, but also points to nuanced differences in how risk is approached under different conceptual framings.
+This suggests that while there may be common ground in economic choices, especially in scenarios with clear, real-world implications, significant differences emerge in how risk is valued and managed, potentially shaped by societal roles, individual experiences, or inherent biases.
+This analysis calls for a deeper understanding of gender perspectives in economic decisions, emphasizing the importance of context in shaping preferences towards risk and stability.
 

### 2024-02-15 scripts/03-test-data-validity.R

@@ -1,7 +1,7 @@
 # Install necessary packages
-# install.packages("dplyr")
-# install.packages("readr")
-# install.packages("here")
+install.packages("dplyr")
+install.packages("readr")
+install.packages("here")
 
 # Load necessary packages
 library(readr)

### 2024-02-15 outputs/paper/paper.qmd
fixed issue

@@
 
+\newpage
 ```{r fig-problem2-male, echo=FALSE, fig.cap="The percentage of male participants' choices ranking each seller in problem 2"}
@@
 
+\newpage
 ```{r fig-problem3-male, echo=FALSE, fig.cap="The percentage of male participants' choices (more, same, less) for both 'buy' and 'sell' conditions in problem 3"}
@@
 
+\newpage
 Observations from @fig-problem4-male for male participants' choices:

### 2024-02-15 outputs/paper/paper.qmd
added fix

@@
 
-Money illusion refers to a cognitive bias where individuals tend to assess the valueof money solely based on its nominal value.
-The real value of money is the nominal value of money plus the inlation rate.
-thereby overlooking the impact of inflation.This bias can lead to various consequences, such as reluctance to sell assets due to perceived nominal losses, misunderstanding wage increases, and more.
+Money illusion refers to the cognitive bias where individuals assess the value of money based on its nominal value, overlooking the impact of inflation.
+This bias can lead to various economic consequences, such as reluctance to sell assets due to perceived nominal losses or misunderstanding wage increases.
+Our study aims to investigate the presence of money illusion in a Brazilian cultural setting, with a particular focus on its relationship with gender.
+This research addresses a gap in the literature by exploring gender-specific responses to money illusion in a Brazilian context, which has not been extensively studied before.
 
-The influential 1997 study by Shafir and colleagues[@shafir1997money] has significantly impacted on economic psychology and behavioral economics which introduced the concept of money illusion.
-The authors argued that money illusion could explain phenomena like inflexible wages and contracts which contrary to traditional economic theories assuming rationality in decision-making.
+In this paper, we emphasize the relationship between gender and money illusion across four problems originally proposed by Shafir and colleagues [@shafir1997money], and then replicated by the Brazilian researchers [@Ferreira_Santiago_Batistuzzo_Seda_Borborema_Fatori_Bastos].
+From a stereotypical perspective, women are often considered more emotional than men in the aspect of luxury consumptions, despite similar functional value to non-luxury brands, luxury brands command higher prices, especially among female consumers[@stokburger2013luxury].
+We hypothesize that gender differences may influence susceptibility to money illusion in various economic scenarios.
 
-When shopping, people often ignore information that is clearly distorted by inflation and impulsively raise the psychological price above the actual price, which is the money illusion.
-Money illusions can lead potential buyers to believe that house prices will always rise, and thus that real estate is a good investment.
-Robert J.
-Shiller, a professor of economics at Yale University in the United States, believes that it is the false logic caused by the monetary illusion that led to the real estate bubble, "people mostly only remember the price of a few years ago when they bought a house, but often forget the price of other goods, andmistakenly believe that house prices have risen more than other prices." Thus exaggerating the investment potential of real estate"[@Shiller_2014].
+Our study's estimand is the effect of gender on susceptibility to money illusion within a Brazilian cultural context.
+We investigate how gender differences influence economic decision-making when individuals are presented with scenarios that typically induce money illusion, such as perceptions of wage increases, real estate transactions, purchasing and selling decisions, and choices between risky and risk-free contracts.
+By replicating four problems originally proposed by Shafir and colleagues [@shafir1997money], we aim to quantify the magnitude of these gender differences and understand their implications for economic behavior.
 
-For decades, economists have debated whether the money illusion is real or, more generally, whether there are irrational influences in economic transactions.Milton Friedman, the famous monetary theorist, assumed that employers and consumers were rational, paying wages or buying goods with inflation in mind.
-In other words, they can accurately judge the true value of a commodity[@friedman2010milton].
+Our findings reveal distinct gender differences in economic decision-making across various scenarios related to money illusion in the Brazilian context.
+Both men and women demonstrated a consensus on economic terms, with a preference for "Carolina," indicating a shared focus on financial stability.
+However, differences emerged in job attractiveness and seller preferences, suggesting gender-specific strategies and priorities in economic exchanges.
+Women exhibited a cautious approach to purchasing and a proactive selling strategy, reflecting a risk-averse attitude, while men showed a balanced approach to buying and selling decisions.
+In terms of contract preferences, both genders favored risk-free contracts in real terms, but men displayed a greater willingness to take risks under nominal terms.
+These findings highlight the multifaceted nature of economic decision-making, where financial stability intersects with career aspirations and risk tolerance in gender-specific ways.
 
-Recognizing the importance of testing theories in different contexts for generalizability, our study aims to investigate the presence of the money illusion effect in a Brazilian cultural setting.
-Specifically, we aim to replicate four problems proposed by Shafir and colleagues [@shafir1997money]and examine if Brazilians exhibit money illusion biases.
+Understanding these gender differences is important as it can inform policymakers and economists about the varying impacts of economic policies and market conditions on different segments of the population.
+It can also contribute to the development of more inclusive and effective financial education programs that address the specific needs and biases of both men and women.
+Overall, our study confirms the presence of money illusion in the Brazilian context and highlights gender differences in economic decision-making across various scenarios.
+This research contributes to a deeper understanding of the complex interplay between cognitive biases, gender, and economic behavior in a culturally diverse setting.
 
-In this paper, we focus on the relationship between sex and money illusion in the four problems.
-According to the references we have found, women is more emotional than men in the aspect of luxury consumptions, despite similar functional value to non-luxury brands, luxury brands command higher prices, especially among female consumers[@stokburger2013luxury].
-
-Our hypothesis are across all four problems: Problem 1, gender and preference in economic decision making; Problem 2, Gender and seller choice; Problem 3, gender and market participation decisions; Problem 4, Gender and financial risk decision making.
-First of all, we choose the dataset from one replication of “Money Illusion”, then we cleaned the dataset and removed all unnecessary variables in dataset.
-We plot the graphs of among four problems for male and female respectively.
-Then we make analysis of it and verify whether we have evidence to against the hypothesis.
-Then we draw the conclusion and list the limitations of our study.
-
-The findings from experiments investigating gender differences in economic decision-making, highlighting distinct behaviors between men and women acrossvarious contexts, such as job attractiveness, seller selection, buying and selling strategies, and preferences for risky or risk-free contracts.
-It reveals that both genders show common concerns for economic stability, yet differ in their evaluation of career opportunities, decision-making strategies, and risk preferences.
-The discussion emphasizes the nuanced role of gender in economic decisions, suggesting further research to explore socio-economic factors, cross-cultural impacts, and psychological dynamics behind these decisions.
-The study acknowledges limitations due to its experimental design and calls for future research employing more comprehensive and realistic approaches to better understand gender influences in economic behavior.
+The paper is structured as follows: Section 2 provides a review of the literature on money illusion and gender differences in economic decision-making.
+Section 3 describes the methodology used in our study, including the replication of the four problems and the data collection process.
+Section 4 presents the results of our analysis, and Section 5 discusses the implications of our findings for theory and practice.
+Finally, Section 6 concludes with a summary of our main contributions and suggestions for future research.
 
@@
 This indicates a strong preference for the economic implications associated with "Maria" among male participants, suggesting they may perceive "Maria" as a more stable or profitable economic choice.
-For the happiness, the male participants' choices for happiness are nearly evenly split, with a slight preference for "Maria." This distribution shows that men do not strongly associate either "Maria" or "Carolina" with happiness or that they see both options as similarly capable of providing emotional satisfaction.
+For the economic terms, a significant majority of male participants chose "Maria" over "Carolina" in economic terms.
+This indicates a strong preference for the economic implications associated with "Maria" among male participants, suggesting they may perceive "Maria" as a more stable or profitable economic choice.
+For the happiness, the male participants' choices for happiness shows a slight preference for "Carolina." This distribution shows that men strongly associate with "Carolina" with happiness which is more capable to provide emotional satisfaction.
+For the job Attractiveness, male participants displayed a clear preference for "Maria" in terms of job attractiveness.
+This could suggest that the attributes or opportunities associated with "Maria" resonate more with men when considering the attractiveness of a job or career path.
 For the job Attractiveness, male participants displayed a clear preference for "Maria" in terms of job attractiveness.
@@
 
-For the buy decisions, males show a balanced approach between buying more and the same, with less likelihood to buy less.
+For the buy decisions, males show a balanced approach between buying less and the same, with less likelihood to buy more.
 For the sell decisions, there is a strong preference for selling the same, followed by selling more, and the least for selling less.
@@
 
-The first experiment focused on exploring how gender affects individuals' decision-making preferences when faced with economic terms and job attractiveness choices.
-The analysis showed that both men and women agreed on their choices regarding economic terms, generally preferring "Carolina," which may reflect a common concern for economic stability across genders.
-However, differences between genders became evident in terms of job attractiveness, with men preferring "Maria," suggesting they have different evaluations of career opportunities and potential for development compared to women.
-The second experiment examined how men and women make choices based on different characteristics of sellers.
-The results indicated that men and women initially preferred different sellers, with men choosing Andre and women choosing Marcelo.
-This finding may reflect different strategies and priorities in economic decision-making between genders.
-As the choices progressed, preferences for sellers converged, especially in the final choice, where Marcelo became the most popular seller.
-The third experiment focused on how gender affects buying and selling decisions, especially under different probability conditions.
-It was observed that women showed a lower likelihood in purchasing decisions and a greater tendency to increase sales, possibly indicating a cautious attitude towards buying and an active strategy towards selling.
-In contrast, men exhibited a more balanced approach to both buying and selling decisions, suggesting a preference for maintaining the status quo rather than making radical adjustments in changing market conditions.
-The fourth experiment delved into how gender influences individual preferences for different types of contracts (risky and risk-free) and different economic terms (real, nominal, neutral).
-Results showed that both men and women preferred risk-free contracts when it came to contracts adjusted for real terms, possibly indicating a common preference to protect purchasing power against inflation.
-However, under nominal terms, men were relatively more inclined to choose risky contracts, revealing a willingness to take risks for higher returns without inflation adjustment.
+The first problem revealed a gender consensus in prioritizing "Maria" for economic advantage, indicating a universal valuation of financial stability.
+However, the divergence in job attractiveness preferences—with men favoring "Maria" for career opportunities—suggests differing gender perspectives on professional development.
+This contrast highlights the multifaceted nature of economic decision-making, where financial stability intersects with career aspirations in gender-specific ways.
+Our second problem delved into seller preferences, uncovering an initial gender disparity with men preferring Andre and women Marcelo.
+This divergence may illustrate distinct gendered strategies or priorities in economic exchanges.
+Remarkably, as the decision process evolved, preferences converged towards Marcelo, suggesting a dynamic reassessment of value and trustworthiness across genders.
+The third problem focused on buying and selling decisions under varying probabilities, where a cautious approach to purchasing and a proactive selling strategy were more pronounced among women.
+This could reflect a gendered risk aversion and a strategic orientation towards asset management.
+Conversely, men's balanced approach to buying and selling decisions hints at a preference for stability over speculative adjustments, indicating a nuanced understanding of market dynamics.
+In our fourth problem, examining preferences for riskier versus risk-free contracts under different economic terms, we observed a shared gender preference for risk-free contracts in real terms.
+This consensus underscores a collective concern for preserving purchasing power.
+However, under nominal terms, men displayed a relative openness to risk, suggesting a gendered divergence in risk tolerance and financial optimism.
 

### 2024-02-15 outputs/paper/paper.qmd
final check

@@
 Our findings reveal distinct gender differences in economic decision-making across various scenarios related to money illusion in the Brazilian context.
-Both men and women demonstrated a consensus on economic terms, with a preference for "Carolina," indicating a shared focus on financial stability.
+Both men and women demonstrated a consensus on economic terms, with a preference for "Maria," indicating a shared focus on financial stability.
 However, differences emerged in job attractiveness and seller preferences, suggesting gender-specific strategies and priorities in economic exchanges.
@@
 
-The data were collected via an online survey platform of and include a range of variables:
+The data were collected via an online survey platform and include a range of variables that capture socio-demographic information and economic decision-making scenarios.
+These scenarios are designed to assess susceptibility to the money illusion, a cognitive bias where individuals assess the value of money based on its nominal value, overlooking the impact of inflation.
+This dataset is particularly relevant for understanding how this bias manifests in a Brazilian cultural setting and how it interacts with gender differences in economic decision-making.
 
@@
 Utilizing identical datasets as the original paper, our analysis narrows the focus to the variable of gender.
+For a sample of this dataset, please refer to the appendix, which includes data tables for each research question.
 
@@
 A cross-sectional online survey was conducted with the prerequisites that participants be at least 18 years old and give their consent.
-The study received ethical clearance from the Pontifical Catholic University of São Paulo's Research Ethics Committee in 2021.
+The study received ethical clearance from the Pontifical Catholic University of São Paulo's Research Ethics Committee in 2021 [@Santiago_Feldman_Ferreira_Batistuzzo_Fatori_Seda_Bastos_2023].
 

### 2024-02-15 outputs/paper/paper.qmd
fixed issue

@@
 
-Observations from @fig-problem2-female for female participants' choices: First Choice:
+Observations from @fig-problem2-female for female participants' choices:
 
@@
 The first problem revealed a gender consensus in prioritizing "Maria" for economic advantage, indicating a universal valuation of financial stability.
-However, the divergence in job attractiveness preferences—with men favoring "Maria" for career opportunities—suggests differing gender perspectives on professional development.
+However, the divergence in job attractiveness preferences, with men favoring "Maria" for career opportunities, suggests differing gender perspectives on professional development.
 This contrast highlights the multifaceted nature of economic decision-making, where financial stability intersects with career aspirations in gender-specific ways.
@@
 
-For Experiment 1, to further understand the role of gender in economic decision-making, future research needs to adopt a more comprehensive approach that considers a broader range of socio-economic factors and individual differences.
+For problem 1, to further understand the role of gender in economic decision-making, future research needs to adopt a more comprehensive approach that considers a broader range of socio-economic factors and individual differences.
 Additionally, studies can explore how gender affects individuals' perceptions of and strategies for dealing with economic risks, and how these differences impact individuals' long-term economic well-being.
@@
 Moreover, qualitative research methods such as in-depth interviews and case studies will help reveal the psychological dynamics and social influences behind decisions, providing richer insights for developing more effective economic policies and educational programs.
-For Experiment 2, future research should explore more factors influencing the choice of sellers, such as the dynamics between sellers and buyers, the impact of marketing strategies, and how personal characteristics of sellers affect buyers' choices.
+For problem 2, future research should explore more factors influencing the choice of sellers, such as the dynamics between sellers and buyers, the impact of marketing strategies, and how personal characteristics of sellers affect buyers' choices.
 By using a more diverse sample of participants, increasing the complexity of scenarios, and applying mixed-methods research designs, our understanding of how gender influences economic decisions can be enhanced.
 Furthermore, considering how cultural and socio-economic factors shape gender roles is also an important direction for future research.
-For Experiment 3, future research needs to explore other variables beyond gender that affect economic decisions and attempt to replicate these findings under more realistic conditions.
+For problem 3, future research needs to explore other variables beyond gender that affect economic decisions and attempt to replicate these findings under more realistic conditions.
 Additionally, studies should consider how cultural differences and social structures shape economic behavior and how education and policy interventions can mitigate the adverse effects of gender differences.
 Through more in-depth quantitative and qualitative research, a more comprehensive understanding of how individuals make decisions in different economic contexts can be achieved.
-For Experiment 4, future research should investigate gender differences across more dimensions, including how education and policy interventions can balance these differences.
+For problem 4, future research should investigate gender differences across more dimensions, including how education and policy interventions can balance these differences.
 Studies could be extended to individuals across different cultural and social backgrounds to explore how cultural factors influence the relationship between gender and economic decisions.

### 2024-02-15 outputs/paper/paper.qmd
Fixed link issue

@@
 Our findings highlight that the effects of money illusion may also vary by gender, showcasing distinct patterns of financial behavior between males and females."
-thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
+thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"
 author: "Terry Tu, Jingyi Shen, Yaning Jin "

### 2024-02-15 outputs/paper/paper.qmd
Fixed abstract issue

@@
 abstract: "Money illusion is a cognitive bias where individuals focus on nominal rather than real values, a concept initially highlighted by Shafir, Diamond, and Tversky (1997).
-In this study, we replicated four scenarios from their research within the Brazilian context, involving 372 participants making financial decisions impacted by money illusion in contexts of earnings and transactions.
-Through our analysis, we found that decision-making was significantly influenced by the framing of information, with notable differences in rationality between genders.
-Our findings highlight that the effects of money illusion may also vary by gender, showcasing distinct patterns of financial behavior between males and females."
+In this study, we replicated four scenarios from their research within the Brazilian context, involving 372 participants, to explore the impact of gender on financial decision-making under the influence of money illusion.
+Our analysis revealed significant gender differences in decision-making, with males and females exhibiting distinct patterns of financial behavior when information was framed differently.
+These findings underscore the importance of considering gender in economic policies and financial education programs, as the effects of money illusion may vary between males and females, influencing their economic decisions and behaviors."
 thanks: "Code and data supporting this analysis are available at https://github.com/TEJMaster/Replication-For-Money-Illusion.git Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1671/published/index"

### 2024-02-15 outputs/paper/paper.qmd
fixed issue

@@
 
-The paper is structured as follows: Section 2 provides a review of the literature on money illusion and gender differences in economic decision-making.
-Section 3 describes the methodology used in our study, including the replication of the four problems and the data collection process.
-Section 4 presents the results of our analysis, and Section 5 discusses the implications of our findings for theory and practice.
-Finally, Section 6 concludes with a summary of our main contributions and suggestions for future research.
+The structure of the paper is organized as follows: Section 2 (Data) describes the data sources, data collection process, and the methodology used for data cleaning and preparation.
+Section 3 (Results) presents the results of our analysis, including the replication of the four problems and the examination of gender differences in responses.
+Section 4 (Discussion) discusses the implications of our findings for theory and practice, highlighting the relevance of money illusion in economic decision-making and the role of gender in shaping economic behaviors.
+Section 5 (Appendix) provides additional details on the methodology, data analysis, and supplementary results that support the main findings of the study, while the Reference section lists the scholarly articles, books, and other sources cited in the paper.
 
@@
 This study serves as a reproduction and further exploration of the seminal work on the money illusion effect, particularly examining the impact of gender on financial decision-making.
-Utilizing identical datasets as the original paper, our analysis narrows the focus to the variable of gender.
-For a sample of this dataset, please refer to the appendix, which includes data tables for each research question.
+Utilizing the same datasets as the original paper, our analysis narrows the focus to the variable gender.
+Data was cleaned using the script `/scripts/02-cleanup-data.R`.
+For data cleaning and view samples of this dataset, please refer to the appendix, which includes data tables for each research question after cleaning.
 
